---
title: "CORE WEBSITE INFORMATION"
author: "Urška Košir"
date: "Last update: `r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
library(here)
library(haven)
library(psych)
library(english)
library(stringr)
library(tableone)
library(kableExtra)
library(patchwork)
library(scales)
library(ggridges)
```

```{r data, echo=FALSE, message=FALSE, warning=FALSE}
# Read in the raw SAS data file from the global sample
global_raw <- read_sas("survey_13/survey_1_13.sas7bdat") %>%
  select_all(tolower)

# Create a unique user ID (single digit)
global_raw <- rowid_to_column(global_raw)

## Extract the dates in order to be able to count participants by month
# variable startdate2 is for year-month only
# variable startdate3 is for year-month-day
global_raw$startdate2<-as.Date(global_raw$startdate)
global_raw$startdate2<- factor(format(global_raw$startdate2,'%Y-%m'))

global_raw$startdate3<-as.Date(global_raw$startdate)
global_raw$startdate3<- factor(format(global_raw$startdate3,'%Y-%m-%d'))

# Create a sub-dateframe for demographics, including renaming the variables for the ease of reading/interpreting
website_dems <- global_raw %>%
  select(rowid, startdate2, startdate_part, wave,
         sex, age_yrs, edu, curemp, area, hoinc, contains("cemplstat")) %>%
  mutate(cempstat = case_when(cemplstat_sq001 == 0 ~ 1,
                              cemplstat_sq001 == 1 ~ 2,
                              cemplstat_sq008 == 1 ~ 3),
        age_group = case_when(age_yrs <=25 ~ "under 25", 
                               age_yrs > 25 & age_yrs <51 ~ "26 - 50y",
                               age_yrs > 50 ~ "over 51"),
        sex = factor(sex, levels = c(1:4),
                      labels = c("male", "female", "other", "prefer not to answer")),
        area = factor(area, levels = c(1:4),
                      labels = c("rural", "suburban", "urban", "prefer not to answer")),
        employment = coalesce(curemp, cempstat),
        employment = factor(employment, 
                            levels = c(1:3),
                            labels = c("no", "yes", "prefer not to answer")),
        hoinc = factor(hoinc, 
                       levels = c(1:4),
                       labels = c("bottom 3rd", "middle 3rd", "top 3rd", "prefer not to answer")),
        edu = factor(edu, 
                     levels = c(1:6),
                     labels = c("primary", "secondary", "college", "graduate", "never been" ,"prefer not to answer"))
         )

# Create a sub-dateframe for health behaviours, including renaming the variables for the ease of reading/interpreting
website_behav <- global_raw %>%
  select(rowid, startdate2, startdate_part, wave,
         actfreq_sq001, actfreq_sq003, actfreq_sq007, actfreq_sq011, actfreq_sq026, actfreq_sq027, actfreq_sq09, actfreq_sq010) %>%
  rename(hand_washing = actfreq_sq001,
         face_mask = actfreq_sq003,
         distancing = actfreq_sq007,
         large_gathering = actfreq_sq011,
         small_gathering = actfreq_sq026,
         indoor_gathering = actfreq_sq027,
         quarantine_travel = actfreq_sq09,
         quarantine_exposure = actfreq_sq010) %>%
  mutate(all_gathering = ifelse((large_gathering==1 & small_gathering==1),1,0))

```

### DEMOGRAPHICS GLOBAL SAMPLE

* Data presented here was collected between March 27, 2020 and `r max(global_raw$startdate, na.rm=TRUE)`

* This data was collected from `r global_raw%>%nrow` people.

* **Self-reported** average age of participants: `r round(mean(global_raw$age_yrs, na.rm=TRUE),1)` years old.

* Participant ages ranged from `r min(global_raw$age_yrs, na.rm=TRUE)` to `r max(global_raw$age_yrs, na.rm=TRUE)`  years old


### DEMOGRAPHICS breakdown

Please include categories "other", "prefer not to answer" and "NA" = missing information somewhere either below each plot or at the bottom of the page.

This is to make the data presentation more transparent and show how many people are represented in the plots.

#### SEX
```{r echo=FALSE, message=FALSE, warning=FALSE}
website_dems%>%
  #filter(sex %in% c("female", "male")) %>%
  count(sex)%>%
  kable()%>%
  kable_styling(full_width = FALSE)
```

#### AGE
```{r echo=FALSE, message=FALSE, warning=FALSE}
website_dems%>%
  #filter(wave %in% c(1:7)) %>%
  count(age_group)%>%
  #drop_na() %>%
  kable()%>%
  kable_styling(full_width = FALSE)
```

#### AREA
```{r echo=FALSE, message=FALSE, warning=FALSE}
website_dems%>%
  #filter(wave %in% c(1:7)) %>%
  #filter(area != "prefer not to answer") %>%
  count(area) %>%
  #drop_na() %>%
  kable()%>%
  kable_styling(full_width = FALSE)
```

#### INCOME
```{r echo=FALSE, message=FALSE, warning=FALSE}
website_dems %>%
  #filter(wave %in% c(1:7)) %>%
  #filter(hoinc != "prefer not to answer") %>%
  count(hoinc)%>%
  #drop_na() %>%
  kable()%>%
  kable_styling(full_width = FALSE)
```

#### EDUCATION
```{r echo=FALSE, message=FALSE, warning=FALSE}
website_dems %>%
  #filter(wave %in% c(1:7)) %>%
  #filter(edu != "prefer not to answer") %>%
  count(edu) %>%
  #drop_na() %>%
  kable() %>%
  kable_styling(full_width = FALSE)
```

#### EMPLOYMENT
```{r echo=FALSE, message=FALSE, warning=FALSE}
website_dems %>%
  #filter(employment != "prefer not to answer") %>%
  count(employment) %>%
  #drop_na() %>%
  kable()%>%
  kable_styling(full_width = FALSE)
```

### Cumulative count to add to the plot

```{r echo=FALSE, message=FALSE, warning=FALSE}
website_dems%>%
  count(startdate2)%>%
  kable(col.names = c("Year-Month", "N"))%>%
  kable_styling(full_width = FALSE)
  
```

## HEALTH BEHAVIOURS

*value of 1 in the column "Most of the time" indicates that it is only people who responded most of the time

### HAND WASHING

```{r echo=FALSE, message=FALSE, warning=FALSE}
website_behav %>%
  pivot_longer(cols = c(hand_washing),
               names_to = "variable") %>%
  group_by(startdate2, variable, value) %>%
  count() %>%
  drop_na() %>%
  filter(value != 5) %>%
  group_by(startdate2, variable) %>%
  mutate(sum_month_status = sum(n),
         prop_most_time = n / sum_month_status * 100) %>%
  filter(value == 1) %>%
  select(-value) %>%
  kable(col.names = c("Year-Month", "Measure", "N yes to most time","Sum of all responses", "% saying most of the time"))%>%
  kable_styling()

```

### FACE MASK

```{r echo=FALSE, message=FALSE, warning=FALSE}
website_behav %>%
  pivot_longer(cols = c(face_mask),
               names_to = "variable") %>%
  group_by(startdate2, variable, value) %>%
  count() %>%
  drop_na() %>%
  filter(value != 5) %>%
  group_by(startdate2, variable) %>%
  mutate(sum_month_status = sum(n),
         prop_most_time = n / sum_month_status * 100) %>%
  filter(value == 1) %>%
  select(-value) %>%
  kable(col.names = c("Year-Month", "Measure", "N yes to most time","Sum of all responses", "% saying most of the time"))%>%
  kable_styling()

```

### DISTANCING

```{r echo=FALSE, message=FALSE, warning=FALSE}
website_behav %>%
  pivot_longer(cols = c(distancing),
               names_to = "variable") %>%
  group_by(startdate2, variable, value) %>%
  count() %>%
  drop_na() %>%
  filter(value != 5) %>%
  group_by(startdate2, variable) %>%
  mutate(sum_month_status = sum(n),
         prop_most_time = n / sum_month_status * 100) %>%
  filter(value == 1) %>%
  select(-value) %>%
  kable(col.names = c("Year-Month", "Measure", "N yes to most time","Sum of all responses", "% saying most of the time"))%>%
  kable_styling()

```

### Large gathering

```{r echo=FALSE, message=FALSE, warning=FALSE}

#all_gathering

website_behav %>%
  pivot_longer(cols = c(large_gathering),
               names_to = "variable") %>%
  group_by(startdate2, variable, value) %>%
  count() %>%
  drop_na() %>%
  group_by(startdate2, variable) %>%
  mutate(sum_month_status = sum(n),
         prop_most_time = n / sum_month_status * 100) %>%
  filter(value == 1) %>%
  select(-value) %>%
  kable(col.names = c("Year-Month", "Measure", "N yes to most time","Sum of all responses", "% saying most of the time"))%>%
  kable_styling()

website_behav %>%
  pivot_longer(cols = c(all_gathering),
               names_to = "variable") %>%
  group_by(startdate2, variable, value) %>%
  count() %>%
  drop_na() %>%
  group_by(startdate2, variable) %>%
  mutate(sum_month_status = sum(n),
         prop_most_time = n / sum_month_status * 100) %>%
  filter(value == 1) %>%
  select(-value) %>%
  kable(col.names = c("Year-Month", "Measure", "N yes to most time","Sum of all responses", "% saying most of the time"))%>%
  kable_styling()

```

### SMALL gathering

```{r echo=FALSE, message=FALSE, warning=FALSE}
website_behav %>%
  pivot_longer(cols = c(small_gathering),
               names_to = "variable") %>%
  group_by(startdate2, variable, value) %>%
  count() %>%
  drop_na() %>%
  group_by(startdate2, variable) %>%
  mutate(sum_month_status = sum(n),
         prop_most_time = n / sum_month_status * 100) %>%
  filter(value == 1) %>%
  select(-value) %>%
  kable(col.names = c("Year-Month", "Measure", "N yes to most time","Sum of all responses", "% saying most of the time"))%>%
  kable_styling()

```

### Plots

See the inconsistencies in gatherings

```{r echo=FALSE, message=FALSE, warning=FALSE}
website_behav %>%
  pivot_longer(cols = c(hand_washing, face_mask, distancing, large_gathering, small_gathering, indoor_gathering),
               names_to = "variable") %>%
  group_by(startdate2, variable, value) %>%
  count() %>%
  group_by(startdate2, variable) %>%
  mutate(sum_month_status = sum(n),
         prop_most_time = n / sum_month_status * 100) %>%
  filter(value == 1) %>%
  ggplot(aes(x = startdate2)) +
  geom_col(aes(y = prop_most_time, fill="blue")) +
  facet_wrap(~variable) +
  labs(title = "Proportion engaging most of the time", x = "Year-month", y = "%") +
  ylim(0, 100) +
  theme_bw() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1))
```


### QUARANTINING

<!-- ```{r echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- website_behav %>% -->
<!--   pivot_longer(cols = c(quarantine_travel, quarantine_exposure), -->
<!--                names_to = "variable") %>% -->
<!--   group_by(startdate2, variable, value) %>% -->
<!--   count() %>% -->
<!--   drop_na() %>% -->
<!--   group_by(startdate2, variable) %>% -->
<!--   mutate(sum_month_status = sum(n), -->
<!--          prop_most_time = n / sum_month_status * 100) %>% -->
<!--   filter(value == 1) %>% -->
<!--   kable(col.names = c("Year-Month", "quarantine reason", "yes", "N yes","Sum of all responses", "% saying yes"))%>% -->
<!--   kable_styling() -->

<!-- ``` -->

<!-- ### PLOTS -->
<!-- ```{r echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- website_behav %>% -->
<!--   pivot_longer(cols = c(quarantine_travel, quarantine_exposure), -->
<!--                names_to = "variable") %>% -->
<!--   group_by(startdate2, variable, value) %>% -->
<!--   count() %>% -->
<!--   group_by(startdate2, variable) %>% -->
<!--   mutate(sum_month_status = sum(n), -->
<!--          prop_most_time = n / sum_month_status * 100) %>% -->
<!--   filter(value == 1) %>% -->
<!--   ggplot(aes(x = startdate2)) + -->
<!--   geom_col(aes(y = prop_most_time, fill="blue")) + -->
<!--   facet_wrap(~variable) + -->
<!--   labs(title = "Proportion quarantining", x = "Year-month", y = "%") + -->
<!--   ylim(0, 100) + -->
<!--   theme_bw() + -->
<!--   theme(legend.position = "none", -->
<!--         axis.text.x = element_text(angle = 45, hjust = 1)) -->
<!-- ``` -->

## QUARANTINE AFTER TRAVEL, wave 1 - 9 ("actfreq_sq009")

```{r echo=FALSE, message=FALSE, warning=FALSE}
website_behav %>%
  filter(quarantine_travel %in% c(1:4)) %>%
  mutate(travel = case_when(quarantine_travel == 1 ~ "Most time",
                          quarantine_travel >1 ~ "Other")) %>%
  select(rowid, startdate2, travel) %>%
  drop_na() %>%
  pivot_longer(cols = c("travel"),
               names_to = "variable",
               values_to = "response") %>%
  group_by(startdate2, variable, response) %>%
  count() %>%
  group_by(startdate2, variable) %>%
  mutate(sum  = sum(n),
         prop = n / sum * 100, 
         prop = round(prop, 2)) %>%
  ungroup() %>%
  select(startdate2, response, n, prop) %>%
  kable(col.names = c("Month", "Response category", "N", "Proportion")) %>%
  kable_styling("hover", full_width = FALSE)

```


## QUARANTINE AFTER EXPOSURE TO VIRUS, wave 1 - 9 ("actfreq_sq010")

```{r echo=FALSE, message=FALSE, warning=FALSE}
website_behav %>%
  filter(quarantine_exposure %in% c(1:4)) %>%
  mutate(quar = case_when(quarantine_exposure == 1 ~ "Most time",
                          quarantine_exposure >1 ~ "Other")) %>%
  select(rowid, startdate2, quar) %>%
  drop_na() %>%
  pivot_longer(cols = c("quar"),
               names_to = "variable",
               values_to = "response") %>%
  group_by(startdate2, variable, response) %>%
  count() %>%
  group_by(startdate2, variable) %>%
  mutate(sum  = sum(n),
         prop = n / sum * 100, 
         prop = round(prop, 2)) %>%
  ungroup() %>%
  select(startdate2, response, n, prop) %>%
  kable(col.names = c("Month", "Response category", "N", "Proportion")) %>%
  kable_styling("hover", full_width = FALSE)

```

## CONTINENTS

Uncommented on Dec 8, 2021. Needed to provide the breakdown for the continents and countries with more than 30 participants.
These numbers are filtered to include Surveys 11 - 13. 
The top panel provide the breakdown between continents. The table below specifies the N in each specific country - refer to ISO codes for country names if unsure.

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(countrycode)
global_raw<-as.data.frame(global_raw)
global_raw$continent <- countrycode(sourcevar = global_raw[, "iso3_code"], ## <- if have earlier data sets this variable did not exist until survey 10 or 11, it changed a few times
                                   origin = "iso3c",
                                   destination = "continent")

global_raw %>%
    filter(wave %in% c(11:13)) %>% ## NB this is filtering out only for the survey 11 - 13
  group_by(startdate2, continent) %>%
  count(startdate2, continent) %>%
  #drop_na() %>%
  pivot_wider(names_from = "startdate2", values_from = "n") %>%
  kable() %>%
  kable_styling("hover")


global_raw %>%
  filter(wave %in% c(11:13)) %>%
  group_by(iso3_code) %>%
  count() %>%
  drop_na() %>%
  filter(n>29) %>%
  kable() %>%
  kable_styling("hover", full_width = FALSE)
```

<!-- ### NOTES related to the code - updated 25/11/2021 -->
<!-- received data update with survey 12 and 13  -->
<!-- had to change some coding from the ealier parts: -->
<!-- - series of cempstat_sq00X variables have been renames to cemplstat_sq00X for consistency purposes
Problem is that the SQ are upper case now, so I had to add lower case conversion again-->