---
title: "Survey 11 - What's new?"
author: "Prepared by: UK"
date: "Last update: `r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
library(here)
library(psych)
library(english)
library(stringr)
library(tableone)
library(kableExtra)
library(patchwork)
library(scales)
library(ggridges)
library(plotly)
library(patchwork)
library(haven)
```

```{r data, echo=FALSE, message=FALSE, warning=FALSE}
# Read in the raw SAS data file from the global sample
global_raw <- read_sas("survey_11/survey_1_11.sas7bdat") %>%
  select_all(tolower)

# Create a unique user ID (single digit)
global_raw <- rowid_to_column(global_raw)

global_raw$startdate2<-as.Date(global_raw$startdate)
global_raw$startdate2<- factor(format(global_raw$startdate2,'%Y-%m')) ## Keep just month and year

global_raw$startdate3 <- as.Date(global_raw$startdate)
global_raw$startdate3<- factor(format(global_raw$startdate3,'%Y-%m-%d')) ## Keep year, month, day

survey_11 <- global_raw %>%
  filter(wave == 11) %>%
  select(rowid, immurec, immuinfl, startdate, startdate2, contains("country"), iso3_code,
         cvdvacci, cvdvacc_v2, contrpos,
         contains("inflvac"), contains("inflvade"),
         sex, age_yrs, edu, curemp, area, hoinc, contains("cempstat")) %>%
  mutate(cempstat = case_when(cempstat_sq001 == 0 ~ 1, ## Create a new variable for binary employment
                              cempstat_sq001 == 1 ~ 2,
                              cempstat_sq008 == 1 ~ 3),
        age_group = case_when(age_yrs <=25 ~ "under 25", 
                               age_yrs > 25 & age_yrs <51 ~ "26 - 50y",
                               age_yrs > 50 ~ "over 51"),
        sex = factor(sex, levels = c(1:4),
                      labels = c("male", "female", "other", "prefer not to answer")),
        area = factor(area, levels = c(1:4),
                      labels = c("rural", "suburban", "urban", "prefer not to answer")),
        employment = coalesce(curemp, cempstat), ## coalesce the values from survey 1-4 and the new variable created above..
        employment = factor(employment, 
                            levels = c(1:3),
                            labels = c("no", "yes", "prefer not to answer")),
        hoinc = factor(hoinc, 
                       levels = c(1:4),
                       labels = c("bottom 3rd", "middle 3rd", "top 3rd", "prefer not to answer")),
        edu = factor(edu, 
                     levels = c(1:6),
                     labels = c("primary", "secondary", "college", "graduate", "never been" ,"prefer not to answer"))
         ) %>%
  mutate(vaccine = factor(cvdvacci, 
                          levels = c(1:5),
                          labels = c("No",
                                     "Yes (partially)",
                                     "Yes (fully)",
                                     "Yes (fully)",
                                     "Pref. not to answer")))
  
```

## DEMOGRAPHICS GLOBAL SAMPLE Survey 11

* Data presented here were collected between `r min(survey_11$startdate, na.rm=TRUE)` and `r max(survey_11$startdate, na.rm=TRUE)`

* This data were collected from `r survey_11%>%nrow` people.

* **Self-reported** average age of participants: `r round(mean(survey_11$age_yrs, na.rm=TRUE),1)` years old.

* Participant ages ranged from `r min(survey_11$age_yrs, na.rm=TRUE)` to `r max(survey_11$age_yrs, na.rm=TRUE)`  years old

* Sample is `r round((survey_11%>%filter(sex=="female")%>%nrow)/(survey_11%>%nrow)*100,1)` % (*N* = `r survey_11%>%filter(sex=="female")%>%nrow`) female

## Where are participants from?

Table 1 shows the breakdown of numbers of participants by continent and month.

Table 2 shows ISO codes of countries that included at least 30 responses.

**Legend**: *ARG* = Argentina, *CAN* = Canada, *CHE* = Switzerland, *COL* = Colombia, *FRA* = France, *IRL* = Ireland

[Source](https://www.iban.com/country-codes)

```{r echo=FALSE, warning=FALSE}
library(countrycode)
survey_11<-as.data.frame(survey_11)
survey_11$continent <- countrycode(sourcevar = survey_11[, "iso3_code"],
                                   origin = "iso3c",
                                   destination = "continent")

survey_11 %>%
  group_by(startdate2, continent) %>%
  count(startdate2, continent) %>%
  #drop_na() %>%
  pivot_wider(names_from = "startdate2", values_from = "n") %>%
  kable() %>%
  kable_styling("hover")


survey_11 %>%
  group_by(iso3_code) %>%
  count() %>%
  drop_na() %>%
  filter(n>29) %>%
  kable() %>%
  kable_styling("hover", full_width = FALSE)
```

## Vaccination rates in Sample 11

*NB* - proportion include missing data (NA)
```{r echo=FALSE, warning=FALSE}
survey_11 %>%
  select(vaccine) %>%
  group_by(vaccine) %>%
  count() %>%
  ungroup()%>%
  mutate(sum = sum(n),
         prop = n/sum,
         prop = round(prop, 2)) %>%
  ungroup() %>%
  select(-sum) %>%
  kable(col.names = c("Vaccinated?", "N", "Proportion")) %>%
  kable_styling("hover", full_width = FALSE)

```

### For those unvaccinated: If COVID-19 vaccine was available to you today, how likely are you to get it?

Only people who responded "No" to the question above (i.e. N = 175) are considered in this question.
```{r echo=FALSE, warning=FALSE}
survey_11 %>%
  filter(vaccine == "No") %>%
  select(cvdvacc_v2) %>%
  mutate(vaccine_today = factor(cvdvacc_v2, 
                          levels = c(1:5),
                          labels = c("Extremely likely",
                                     "Somewhat likely",
                                     "Somewhat unlikely",
                                     "Extremely unlikely",
                                     "Pref. not to answer"))) %>%
  group_by(vaccine_today) %>%
  count() %>%
  ungroup() %>%
  mutate(sum = sum(n),
         prop = n/sum,
         prop = round(prop, 2)) %>%
  ungroup() %>%
  select(-sum) %>%
  kable(col.names = c("Likelihood", "N", "Proportion")) %>%
  kable_styling(full_width = FALSE)
```

***
# IMMUNIZATION PASSPORTS

The question of immunization passports has been popular already in Survey 9 and 10. We decided to inspect the answers again, this time for those who were *not vaccinated* and provided responses.

## To what extent would the introduction of ‘immunity passports’ influence your decision to get vaccinated?

```{r fig.width=8, fig.height=6, echo=FALSE, message=FALSE}
survey_11 %>%
  filter(vaccine == "No") %>%
  select(immuinfl) %>%  
  drop_na() %>%
  filter(immuinfl %in% c(1:3)) %>%
  pivot_longer(cols = immuinfl,
               names_to = "var", 
               values_to = "response") %>%
  ggplot(aes(x = response, 
             y = (..count..)/154,
             fill = factor(response))) +
  scale_y_continuous(labels=scales::percent, limits = c(0,0.75)) +
  geom_bar() +
  scale_x_continuous(breaks = c(1,2,3),
                   labels = c("More likely to get vaccinated", "No influence", "Less likely to get vaccinated")) +
  theme_bw() +
  scale_fill_viridis_d()+
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = " ",
       y = " Proportion",
       title = "Immunity passport influence on getting vaccinated for the NON-VACCINATED (N = 154)")

```

### Table corresponding to the plot

1 = It would make me more likely to get vaccinated
2 = No influence
3 = Less likely to get vaccinated

```{r echo=FALSE, message=FALSE}
survey_11 %>%
  filter(vaccine == "No") %>%
  select(immuinfl) %>%  
  drop_na() %>%
  filter(immuinfl %in% c(1:3)) %>%
  group_by(immuinfl) %>%
  count() %>%
  mutate(prop = (n/154)*100,
         prop = round(prop, 2)) %>%
  kable(col.names = c("Level of influence", "N", "Proportion")) %>%
  kable_styling(full_width = FALSE)
```


## NEW VARIABLES added to the Survey 11

### VACCINE BOOSTERS: If a booster dose of vaccine (an extra administration of a vaccine after an earlier dose) was required, how likely are you to get it? 

Missing data (NA values) are accounted for when calculating the proportion. 

```{r echo=FALSE, message=FALSE}
global_raw %>%
  filter(wave==11) %>%
  select(vacboos) %>%
  mutate(booster = factor(vacboos, 
                          levels = c(1:5),
                          labels = c("Extremely likely",
                                     "Somewhat likely",
                                     "Somewhat unlikely",
                                     "Extremely unlikely",
                                     "Pref. not to answer"))) %>%
  group_by(booster) %>%
  count() %>%
  ungroup() %>%
  mutate(sum = sum(n),
         prop = n/sum,
         prop = round(prop, 2)) %>%
  ungroup() %>%
  select(-sum) %>%
  kable(col.names = c("Likelihood", "N", "Proportion")) %>%
  kable_styling("hover", full_width = FALSE)

```

### VACCINATION & CHILDREN
#### Have any of your children under 18 years of age received a COVID-19 vaccine?

```{r echo=FALSE, message=FALSE}
global_raw %>%
  filter(wave==11) %>%
  select(vacckid) %>%
  mutate(vacckid = factor(vacckid, 
                          levels = c(1:5),
                          labels = c("No",
                                     "Yes, partially",
                                     "Yes, fully",
                                     "Yes, fully",
                                     "Pref. not to answer"))) %>%
  group_by(vacckid) %>%
  drop_na() %>%
  count() %>%
  ungroup() %>%
  mutate(sum = sum(n),
         prop = n/sum,
         prop = round(prop, 2)) %>%
  ungroup() %>%
  select(-sum) %>%
  kable(col.names = c("Response", "N", "Proportion")) %>%
  kable_styling("hover", full_width = FALSE)

```

#### If a vaccine for COVID-19 were available for your child/children, what is the likelihood that you would get them vaccinated?

```{r echo=FALSE, message=FALSE}
global_raw %>%
  filter(wave==11) %>%
  select(vackidin) %>%
  mutate(vackidin = factor(vackidin, 
                          levels = c(1:5),
                          labels = c("Extremely likely",
                                     "Somewhat likely",
                                     "Somewhat unlikely",
                                     "Extremely unlikely",
                                     "Pref. not to answer"))) %>%
  group_by(vackidin) %>%
  drop_na() %>%
  count() %>%
  ungroup() %>%
  mutate(sum = sum(n),
         prop = n/sum,
         prop = round(prop, 2)) %>%
  ungroup() %>%
  select(-sum) %>%
  kable(col.names = c("Likelihood", "N", "Proportion")) %>%
  kable_styling("hover", full_width = FALSE)

```

## MOTIVATION TO VACCINATE KIDS

The plot is broken down by parental attitudes about vaccinating their children if there was a vaccine available* (data collected prior approval of vaccines for individuals younger than age 12)

The plots are showing number of people responding to a great extent to each individual item. The x axis is fixed for the ease of comparison.
```{r echo=FALSE, warning=FALSE, fig.width=10, fig.height=8}
# Prepare the data needed for the plot, keep the motivators for kids + likelihood to vax kids
vax_kids_data <- global_raw %>%
  filter(wave == 11) %>%
  select(contains("infvakid"), contains("infdekid"), vackidin) %>%
  select_all(tolower) %>%
  mutate(inf1 = coalesce(infvakid_sq001, infdekid_sq001),
         inf2 = coalesce(infvakid_sq002, infdekid_sq002),
         inf3 = coalesce(infvakid_sq003, infdekid_sq003),
         inf4 = coalesce(infvakid_sq004, infdekid_sq004),
         inf5 = coalesce(infvakid_sq021, infdekid_sq021),
         inf6 = coalesce(infvakid_sq012, infdekid_sq012),
         inf7 = coalesce(infvakid_sq013, infdekid_sq013),
         inf8 = coalesce(infvakid_sq015, infdekid_sq015),
         inf9 = coalesce(infvakid_sq016, infdekid_sq016),
         inf10 = coalesce(infvakid_sq007, infdekid_sq007),
         inf11 = coalesce(infvakid_sq010, infdekid_sq010),
         inf12 = coalesce(infvakid_sq011, infdekid_sq011),
         inf13 = coalesce(infvakid_sq017, infdekid_sq017),
         inf14 = coalesce(infvakid_sq018, infdekid_sq018),
         inf15 = coalesce(infvakid_sq022, infdekid_sq022),
         inf16 = coalesce(infvakid_sq020, infdekid_sq020),
         vackidin = as.factor(case_when(vackidin == 1 | vackidin == 2 ~ "Likely",
                                        vackidin == 3 | vackidin == 4 ~ "Unlikely"))) %>%
  select(inf1:inf16, vackidin) %>%
  mutate_at(vars(c(inf1:inf16)), 
            funs(case_when(. == 1 ~ 1,
                           . == 2 | . == 3 | . == 4 ~ 0))) 



## Plots 1 - those responding likely ot vax their kids
likely <- vax_kids_data %>%
  filter(vackidin == "Likely") %>%
  pivot_longer(names_to = "influence", values_to = "value", cols = c(inf1:inf16)) %>%
  group_by(influence, value) %>%
  count(influence) %>%
  drop_na() %>%
  ungroup(influence, value) %>%
  filter(value == 1) %>%
  select(-value) %>%
  mutate(influence = as.factor(influence),
         influence = fct_reorder(influence, n)) %>%
  ggplot(aes(x = n, y = influence, fill = influence)) + 
  geom_col() + 
  scale_x_continuous(limits = c(0,60), n.breaks = 12) +
  labs(title = "Motivations to vaccinate kids for those who are likely to do so (N = 57)", 
       x = " ",
       y = " ") + 
  theme_classic(base_size = 12) +
  theme(legend.position = "none",
        strip.text = element_text(face = 'bold'),
        panel.grid.major.x = element_line()) +
  scale_y_discrete(breaks = c("inf1", "inf2", "inf3", "inf4", "inf5", "inf6", "inf7", "inf8",
                              "inf9", "inf10", "inf11", "inf12", "inf13", "inf14", "inf15", "inf16"),
                   labels = c("Trust in vaccine company",
                              "Info of no side effects",
                              "Info about effectiveness",
                              "Child is high risk",
                              "Back to school in person",
                              "Going to resto",
                              "Doing my part",
                              "Only need 1 dose",
                              "Less worry about kid",
                              "MDs recommendation",
                              "Convenience of getting vaccine",
                              "Protect others and fam.",
                              "Effective for variants",
                              "Vaccine of choice",
                              "Suggested timing",
                              "Clear, consistent info")) +
  scale_fill_viridis_d()

## Second plot - showing the unlikely, I fixed the limits of x axis for ease of reading and comparing the 2 plots
unlikely <- vax_kids_data %>%
  filter(vackidin == "Unlikely") %>%
  pivot_longer(names_to = "influence", values_to = "value", cols = c(inf1:inf16)) %>%
  group_by(influence, value) %>%
  count(influence) %>%
  drop_na() %>%
  ungroup(influence, value) %>%
  filter(value == 1) %>%
  select(-value) %>%
  mutate(influence = as.factor(influence),
         influence = fct_reorder(influence, n)) %>%
  ggplot(aes(x = n, y = influence, fill = influence)) + 
  geom_col() + 
  scale_x_continuous(limits = c(0,60), n.breaks = 12) +
  labs(title = "Motivations to vaccinate kids for those who are UN-likely to do so (N = 57)", 
       x = "Number of people responding 'To a great extent",
       y = " ") + 
  theme_classic(base_size = 12) +
  theme(legend.position = "none",
        strip.text = element_text(face = 'bold'),
        panel.grid.major.x = element_line()) +
  scale_y_discrete(breaks = c("inf1", "inf2", "inf3", "inf4", "inf5", "inf6", "inf7", "inf8",
                              "inf9", "inf10", "inf11", "inf12", "inf13", "inf14", "inf15", "inf16"),
                   labels = c("Trust in vaccine company",
                              "Info of no side effects",
                              "Info about effectiveness",
                              "Child is high risk",
                              "Back to school in person",
                              "Going to resto",
                              "Doing my part",
                              "Only need 1 dose",
                              "Less worry about kid",
                              "MDs recommendation",
                              "Convenience of getting vaccine",
                              "Protect others and fam.",
                              "Effective for variants",
                              "Vaccine of choice",
                              "Suggested timing",
                              "Clear, consistent info")) +
  scale_fill_viridis_d()

(likely / unlikely) + plot_annotation(tag_levels = 'A')
```
