---
title: "Survey 10 Results"
author: " "
date: "Last update: `r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
library(here)
library(psych)
library(english)
library(stringr)
library(tableone)
library(kableExtra)
library(patchwork)
library(scales)
library(ggridges)
library(plotly)
library(patchwork)
library(haven)

# NB - anyone reading the code, the variables for country have changed names several times therefore in order to have this code run, you need to plug in data only up to survey 10

# If you work with later data, just note the country variable changes in the document and adapt the code accordingly e.g. line 47 - no more "county_iso"

# NB - There is a package iCAREstudy that needs to be updated, in the interim, the code contains a function for pie chart to circumvent this issue
```

```{r data, echo=FALSE, message=FALSE, warning=FALSE}
# Read in the raw SAS data file from the global sample
global_raw <- read_sas("survey_10/wave_10.sas7bdat") %>%
  select_all(tolower)

# Create a unique user ID (single digit)
global_raw <- rowid_to_column(global_raw)


global_raw$startdate2<-as.Date(global_raw$startdate)
global_raw$startdate2<- factor(format(global_raw$startdate2,'%Y-%m')) ## Keep just month and year

global_raw$startdate3 <- as.Date(global_raw$startdate)
global_raw$startdate3<- factor(format(global_raw$startdate3,'%Y-%m-%d')) ## Keep year, month, day

survey_10 <- global_raw %>%
  filter(wave == 10) %>%
  select(rowid, immurec, immuinfl, startdate, country_iso,
         cvdvacci, cvdvacc_v2, contrpos,
         contains("inflvac"), contains("inflvade"),
         sex, age_yrs, edu, curemp, area, hoinc, contains("cempstat")) %>%
  mutate(cempstat = case_when(cempstat_sq001 == 0 ~ 1, ## Create a new variable for binary employment
                              cempstat_sq001 == 1 ~ 2,
                              cempstat_sq008 == 1 ~ 3),
        age_group = case_when(age_yrs <=25 ~ "under 25", 
                               age_yrs > 25 & age_yrs <51 ~ "26 - 50y",
                               age_yrs > 50 ~ "over 51"),
        sex = factor(sex, levels = c(1:4),
                      labels = c("male", "female", "other", "prefer not to answer")),
        area = factor(area, levels = c(1:4),
                      labels = c("rural", "suburban", "urban", "prefer not to answer")),
        employment = coalesce(curemp, cempstat), ## coalesce the values from survey 1-4 and the new variable created above..
        employment = factor(employment, 
                            levels = c(1:3),
                            labels = c("no", "yes", "prefer not to answer")),
        hoinc = factor(hoinc, 
                       levels = c(1:4),
                       labels = c("bottom 3rd", "middle 3rd", "top 3rd", "prefer not to answer")),
        edu = factor(edu, 
                     levels = c(1:6),
                     labels = c("primary", "secondary", "college", "graduate", "never been" ,"prefer not to answer"))
         ) %>%
  mutate(vaccine = factor(cvdvacci, 
                          levels = c(1:5),
                          labels = c("No",
                                     "Yes (partially)",
                                     "Yes (fully)",
                                     "Yes (fully)",
                                     "Pref. not to answer")))
  

plot_pie_chart <- function(data,
                           variable,
                           filter_response = NULL,
                           title = NULL,
                           filllab = NULL,
                           labels = NULL,
                           number_font_size = 4,
                           return = c("plot", "data")) {

  return <- match.arg(return)

  data$month<-as.Date(data$startdate)
  data$month<- factor(format(data$month,'%Y-%m'))

  data_temp <- data %>%
    dplyr::select({{variable}}) %>%
    tidyr::pivot_longer(cols = {{variable}},
                 names_to = "variable") %>%
    dplyr::group_by(variable, value) %>%
    dplyr::count() %>%
    tidyr::drop_na() %>%
    dplyr::group_by(variable)%>%
    dplyr::mutate(sum_group = sum(n),
           prop = n / sum_group * 100)

  if(is.null(filter_response)) {
    data_temp <- data_temp
  } else
  {data_temp <- data_temp %>%
    dplyr::filter(value %in% filter_response)
  }
  # set the theme for the plot
  blank_theme <- ggplot2::theme_minimal()+
    ggplot2::theme(axis.title.x = ggplot2::element_blank(),
          axis.title.y = ggplot2::element_blank(),
          panel.border = ggplot2::element_blank(),
          panel.grid = ggplot2::element_blank(),
          axis.ticks = ggplot2::element_blank(),
          axis.text.x = ggplot2::element_blank(),
          plot.title = ggplot2::element_text(size = 15, hjust = 0.5, vjust = 1))

  plot <- data_temp %>%
    ggplot(aes(x =  "", y = n, fill = factor(value)))+
    geom_bar(stat = "identity") +
    coord_polar("y", start = 0)+
    labs(fill = filllab, title = title) +
    blank_theme +
    geom_text(aes(label = paste(round(n / sum(n) * 100, 1), "%")),
              color = "black", size = number_font_size,
              position = position_stack(vjust = 0.5))

  if(return == "data"){

    return(data_temp)

  }
  if(return == "plot"){
    if(is.null(labels)){
      return(plot)
    }else{
      return(plot + scale_fill_discrete(labels = labels))
    }
  }
}

```

# IMMUNIZATION PASSPORTS

## Immunization or vaccination passports have been suggested as a way to safely resume international travel. 
## How do you feel about the idea of using an immunization or vaccination passports?

```{r fig.width=8, fig.height=6, echo=FALSE, message=FALSE}
global_raw %>%
  filter(wave == 10) %>%
  select(immurec) %>%   # immuinfl
  drop_na() %>%
  filter(immurec %in% c(1:4)) %>%
  pivot_longer(cols = immurec,
               names_to = "var", 
               values_to = "response") %>%
  ggplot(aes(x = response, 
             y = (..count..)/976,
             fill = factor(response))) +
  scale_y_continuous(labels=scales::percent, limits = c(0,0.75)) +
  geom_bar() +
  scale_x_continuous(breaks = c(1,2,3,4),
                   labels = c("Strongly in favor", "Moderately in favor", "Moderately against", "Strongly against")) +
  theme_bw() +
  scale_fill_viridis_d()+
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = " ",
       y = " Proportion",
       title = "Immunity passport attitudes (N = 976)")

```

### Table corresponding to the graph above

1 = Strongly in favor

```{r echo=FALSE, message=FALSE}
global_raw %>%
  filter(wave == 10) %>%
  select(immurec) %>%   # immuinfl
  drop_na() %>%
  filter(immurec %in% c(1:4)) %>%
  group_by(immurec) %>%
  count() %>%
  mutate(prop = (n/976)*100,
         prop = round(prop, 2)) %>%
  kable() %>%
  kable_styling(full_width = FALSE)
```

## ATTITUDES BY DEMOGRAPHICS

Just like for Survey 9, we would like to have the above plotted by various demographics, the numbers are shown below in separate tables.

**We would like to include proportion numbers (%) in the plots as well.**

### SEX
```{r echo=FALSE, warning=FALSE}
survey_10 %>%
  filter(immurec %in% c(1:4)) %>%
  mutate(immurec = factor(immurec, 
                          levels = c(1:4),
                          labels = c("strongly in favor", "moderately in favor", "moderately against", "strongly against"))) %>%
  filter(sex %in% c("male", "female")) %>%
  group_by(sex, immurec) %>%
  count() %>%
  group_by(sex) %>%
  mutate(sum = sum(n),
         prop = n/sum,
         prop = round(prop, 2)) %>%
  ungroup() %>%
  select(-sum) %>%
  kable() %>%
  kable_styling("hover", full_width = FALSE)
```

### AGE GROUP
```{r echo=FALSE, warning=FALSE}
survey_10 %>%
  filter(immurec %in% c(1:4)) %>%
  mutate(immurec = factor(immurec, 
                          levels = c(1:4),
                          labels = c("strongly in favor", "moderately in favor", "moderately against", "strongly against"))) %>%
  filter(age_group %in% c("under 25", "26 - 50y","over 51")) %>%
  group_by(age_group, immurec) %>%
  count() %>%
  group_by(age_group) %>%
  mutate(sum = sum(n),
         prop = n/sum,
         prop = round(prop, 2)) %>%
  ungroup() %>%
  select(-sum) %>%
  kable() %>%
  kable_styling("hover", full_width = FALSE)
```

### EDUCATION
```{r echo=FALSE, warning=FALSE}
survey_10 %>%
  filter(immurec %in% c(1:4)) %>%
  mutate(immurec = factor(immurec, 
                          levels = c(1:4),
                          labels = c("strongly in favor", "moderately in favor", "moderately against", "strongly against"))) %>%
  filter(edu %in% c("primary", "secondary", "college", "graduate", "never been")) %>%
  group_by(edu, immurec) %>%
  count() %>%
  group_by(edu) %>%
  mutate(sum = sum(n),
         prop = n/sum,
         prop = round(prop, 2)) %>%
  ungroup() %>%
  select(-sum) %>%
  kable() %>%
  kable_styling("hover", full_width = FALSE)
```


### INCOME
```{r echo=FALSE, warning=FALSE}
survey_10 %>%
  filter(immurec %in% c(1:4)) %>%
  mutate(immurec = factor(immurec, 
                          levels = c(1:4),
                          labels = c("strongly in favor", "moderately in favor", "moderately against", "strongly against"))) %>%
  filter(hoinc %in% c("bottom 3rd", "middle 3rd", "top 3rd")) %>%
  group_by(hoinc, immurec) %>%
  count() %>%
  group_by(hoinc) %>%
  mutate(sum = sum(n),
         prop = n/sum,
         prop = round(prop, 2)) %>%
  ungroup() %>%
  select(-sum) %>%
  kable() %>%
  kable_styling("hover", full_width = FALSE)
```

***


## To what extent would the introduction of ‘immunity passports’ influence your decision to get vaccinated?

Same as above, the plot below shows the overall sample, the subsequent tables are breaking it down by the demographic variables. Again, this is all the same as survey 9, just reproduced with data from Survey 10.

```{r fig.width=8, fig.height=6, echo=FALSE, message=FALSE}
global_raw %>%
  filter(wave == 10) %>%
  select(immuinfl) %>%  
  drop_na() %>%
  filter(immuinfl %in% c(1:3)) %>%
  pivot_longer(cols = immuinfl,
               names_to = "var", 
               values_to = "response") %>%
  ggplot(aes(x = response, 
             y = (..count..)/954,
             fill = factor(response))) +
  scale_y_continuous(labels=scales::percent, limits = c(0,0.75)) +
  geom_bar() +
  scale_x_continuous(breaks = c(1,2,3),
                   labels = c("More likely to get vaccinated", "No influence", "Less likely to get vaccinated")) +
  theme_bw() +
  scale_fill_viridis_d()+
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = " ",
       y = " Proportion",
       title = "Immunity passport influence on getting vaccinated (N = 954)")

```

### Table corresponding to the plot

1 = It would make me more likely to get vaccinated

```{r echo=FALSE, message=FALSE}
global_raw %>%
  filter(wave == 10) %>%
  select(immuinfl) %>%   # immuinfl
  drop_na() %>%
  filter(immuinfl %in% c(1:3)) %>%
  group_by(immuinfl) %>%
  count() %>%
  mutate(prop = (n/976)*100,
         prop = round(prop, 2)) %>%
  kable() %>%
  kable_styling(full_width = FALSE)
```

### Vaccine status
```{r echo=FALSE, warning=FALSE}
survey_10 %>%
  filter(immuinfl %in% c(1:3)) %>%
  mutate(immuinfl = factor(immuinfl, 
                          levels = c(1:3),
                          labels = c("more likely to get vaccinated", "no influence", "less likely"))) %>%
  filter(sex %in% c("male", "female")) %>%
  group_by(vaccine, immuinfl) %>%
  count() %>%
  group_by(vaccine) %>%
  mutate(sum = sum(n),
         prop = n/sum,
         prop = round(prop, 2)) %>%
  ungroup() %>%
  select(-sum) %>%
  kable() %>%
  kable_styling("hover", full_width = FALSE)
```

### SEX
```{r echo=FALSE, warning=FALSE}
survey_10 %>%
  filter(immuinfl %in% c(1:3)) %>%
  mutate(immuinfl = factor(immuinfl, 
                          levels = c(1:3),
                          labels = c("more likely to get vaccinated", "no influence", "less likely"))) %>%
  filter(sex %in% c("male", "female")) %>%
  group_by(sex, immuinfl) %>%
  count() %>%
  group_by(sex) %>%
  mutate(sum = sum(n),
         prop = n/sum,
         prop = round(prop, 2)) %>%
  ungroup() %>%
  select(-sum) %>%
  kable() %>%
  kable_styling("hover", full_width = FALSE)
```

### AGE GROUP
```{r echo=FALSE, warning=FALSE}
survey_10 %>%
  filter(immuinfl %in% c(1:3)) %>%
  mutate(immuinfl = factor(immuinfl, 
                          levels = c(1:3),
                          labels = c("more likely to get vaccinated", "no influence", "less likely"))) %>%
  filter(age_group %in% c("under 25", "26 - 50y","over 51")) %>%
  group_by(age_group, immuinfl) %>%
  count() %>%
  group_by(age_group) %>%
  mutate(sum = sum(n),
         prop = n/sum,
         prop = round(prop, 2)) %>%
  ungroup() %>%
  select(-sum) %>%
  kable() %>%
  kable_styling("hover", full_width = FALSE)
```

### EDUCATION
```{r echo=FALSE, warning=FALSE}
survey_10 %>%
  filter(immuinfl %in% c(1:3)) %>%
  mutate(immuinfl = factor(immuinfl, 
                          levels = c(1:3),
                          labels = c("more likely to get vaccinated", "no influence", "less likely"))) %>%
  filter(edu %in% c("primary", "secondary", "college", "graduate", "never been")) %>%
  group_by(edu, immuinfl) %>%
  count() %>%
  group_by(edu) %>%
  mutate(sum = sum(n),
         prop = n/sum,
         prop = round(prop, 2)) %>%
  ungroup() %>%
  select(-sum) %>%
  kable() %>%
  kable_styling("hover", full_width = FALSE)
```


### INCOME
```{r echo=FALSE, warning=FALSE}
survey_10 %>%
  filter(immuinfl %in% c(1:3)) %>%
  mutate(immuinfl = factor(immuinfl, 
                          levels = c(1:3),
                          labels = c("more likely to get vaccinated", "no influence", "less likely"))) %>%
  filter(hoinc %in% c("bottom 3rd", "middle 3rd", "top 3rd")) %>%
  group_by(hoinc, immuinfl) %>%
  count() %>%
  group_by(hoinc) %>%
  mutate(sum = sum(n),
         prop = n/sum,
         prop = round(prop, 2)) %>%
  ungroup() %>%
  select(-sum) %>%
  kable() %>%
  kable_styling("hover", full_width = FALSE)
```
***

## Demographcics overall - Who responded to survey 10

This is mostly informative - given that the separate plots already break down the responses by demographics, this could just be place informatively at the bottom/smaller print.

Again, some numbers might not exactly add up due to missing information.

### Sex

1 = male, 2 = female

```{r echo=FALSE, message=FALSE}
dems<-global_raw %>%
  filter(wave == 10) %>%
  select(sex, startdate, age_yrs, country_iso, hoinc, immuinfl, immurec, cvdvacci) %>%   # immuinfl
  drop_na(sex, startdate, age_yrs, country_iso, hoinc) %>%
  filter(immuinfl %in% c(1:3)) %>%
  filter(immurec %in% c(1:4)) %>%
  mutate(age_group = case_when(age_yrs < 26 ~ 1,
                               age_yrs > 25 & age_yrs <56 ~ 2,
                               age_yrs > 55 ~ 3))

plot_pie_chart(data = dems,
               variable = sex,
               filter_response=c(1:2),
               title = "Sex distribution",
               labels = c("Male", "Female"),
               number_font_size = 6,
               return = "data")

```
### Age

age groups: 1 = under 26, 2 = 26-55y, 3 = over 55
```{r echo=FALSE, message=FALSE}
plot_pie_chart(data = dems,
               variable = age_group,
               filter_response=c(1:3),
               title = "Age groups",
               labels = c("under 26", " 26-55", "over 55"),
               number_font_size = 4,
               return = "data")
```

### Income

1 = lower 3rd, 2 = middle 3rd, 3 = upper 3rd
```{r echo=FALSE, message=FALSE}
plot_pie_chart(data = dems,
               variable = hoinc,
               filter_response=c(1:3),
               title = "Income distribution",
               labels = c("lower 3rd", "middle 3rd", "top 3rd"),
               number_font_size = 4,
               return = "data")
```


# **NEW**: ATTITUDES in CANADA (N = 395)

### How do you feel about the idea of using an immunization or vaccination passports?

```{r echo=FALSE, warning=FALSE}
survey_10 %>%
  filter(country_iso == "CANADA") %>%
  select(immurec) %>%   # immuinfl
  drop_na() %>%
  filter(immurec %in% c(1:4)) %>%
  mutate(immurec = factor(immurec, 
                          levels = c(1:4),
                          labels = c("strongly in favor", "moderately in favor", "moderately against", "strongly against"))) %>%
  group_by(immurec) %>%
  count() %>%
  mutate(prop = (n/317)*100,
         prop = round(prop, 2)) %>%
  kable() %>%
  kable_styling(full_width = FALSE)
```

### To what extent would the introduction of ‘immunity passports’ influence your decision to get vaccinated?

```{r echo=FALSE, warning=FALSE}
survey_10 %>%
  filter(country_iso == "CANADA") %>%
  select(immuinfl) %>%   # immuinfl
  drop_na() %>%
  filter(immuinfl %in% c(1:3)) %>%
  mutate(immuinfl = factor(immuinfl, 
                          levels = c(1:3),
                          labels = c("more likely to get vaccinated", "no influence", "less likely"))) %>%
  group_by(immuinfl) %>%
  count() %>%
  mutate(prop = (n/316)*100,
         prop = round(prop, 2)) %>%
  kable() %>%
  kable_styling(full_width = FALSE)
```

# ADDITIONAL for Survey 10

Most of the data for survey 10 were collected in May and June. Availability of vaccine in Canada was widespread then.

### CANADA: Have you received a COVID-19 vaccine?

```{r echo=FALSE, warning=FALSE}
survey_10 %>%
  filter(country_iso == "CANADA") %>%
  select(cvdvacci) %>%
  mutate(vaccine = factor(cvdvacci, 
                          levels = c(1:5),
                          labels = c("No",
                                     "Yes (partially)",
                                     "Yes (fully)",
                                     "Yes (fully)",
                                     "Pref. not to answer"))) %>%
  group_by(vaccine) %>%
  count() %>%
  ungroup() %>%
  mutate(sum = sum(n),
         prop = n/sum,
         prop = round(prop, 2)) %>%
  ungroup() %>%
  select(-sum) %>%
  kable() %>%
  kable_styling(full_width = FALSE)

```

### CANADA: If COVID-19 vaccine was available to you today, how likely are you to get it?

```{r echo=FALSE, warning=FALSE}
survey_10 %>%
  filter(country_iso == "CANADA") %>%
  select(cvdvacc_v2) %>%
  mutate(vaccine_today = factor(cvdvacc_v2, 
                          levels = c(1:5),
                          labels = c("Extremely likely",
                                     "Somewhat likely",
                                     "Somewhat unlikely",
                                     "Extremely unlikely",
                                     "Pref. not to answer"))) %>%
  group_by(vaccine_today) %>%
  count() %>%
  ungroup() %>%
  mutate(sum = sum(n),
         prop = n/sum,
         prop = round(prop, 2)) %>%
  ungroup() %>%
  select(-sum) %>%
  kable() %>%
  kable_styling(full_width = FALSE)
```

### CANADA: What does/would greatly impact your choice for getting the COVID-19 vaccine?

We wanted to showcase the differences in motivations between those who are vaccinated versus not.

```{r echo=FALSE, warning=FALSE, fig.width=7, fig.height=10}
no <- survey_10 %>%
  filter(country_iso == "CANADA") %>%
  select(cvdvacci, contains("inflvac"), contains("inflvade")) %>%
  select_all(tolower) %>%
  mutate(inf1 = coalesce(inflvac_sq001, inflvade_sq001),
         inf2 = coalesce(inflvac_sq002, inflvade_sq002),
         inf3 = coalesce(inflvac_sq003, inflvade_sq003),
         inf4 = coalesce(inflvac_sq004, inflvade_sq004),
         inf5 = coalesce(inflvac_sq005, inflvade_sq005),
         inf6 = coalesce(inflvac_sq006, inflvade_sq006),
         inf7 = coalesce(inflvac_sq007, inflvade_sq007),
         inf10 = coalesce(inflvac_sq010, inflvade_sq010),
         inf11 = coalesce(inflvac_sq011, inflvade_sq011),
         inf12 = coalesce(inflvac_sq012, inflvade_sq012),
         inf13 = coalesce(inflvac_sq013, inflvade_sq013),
         inf14 = coalesce(inflvac_sq014, inflvade_sq014),
         inf15 = coalesce(inflvac_sq015, inflvade_sq015),
         inf16 = coalesce(inflvac_sq016, inflvade_sq016),
         inf17 = coalesce(inflvac_sq017, inflvade_sq017),
         inf18 = coalesce(inflvac_sq018, inflvade_sq018),
         vaccine = factor(cvdvacci, 
                          levels = c(1:5),
                          labels = c("No",
                                     "Yes (partially)",
                                     "Yes (fully)",
                                     "Yes (fully)",
                                     "Pref. not to answer"))) %>%
  filter(vaccine == "No") %>%
  mutate_at(vars(c(inf1:inf18)), 
            funs(case_when(. == 1 ~ 1,
                           . == 2 | . == 3 | . == 4 ~ 0))) %>%
  pivot_longer(names_to = "influence", values_to = "value", cols = c(inf1:inf18)) %>%
  group_by(influence, value) %>%
  count(influence) %>%
  drop_na() %>%
  ungroup(influence, value) %>%
  filter(value == 1) %>%
  select(-value) %>%
  mutate(influence = as.factor(influence),
         influence = fct_reorder(influence, n)) %>%
  ggplot(aes(x = n, y = influence, fill = influence)) + 
  geom_col() + 
  labs(title = "UNVACCINATED INDIVIDUALS", 
       x = "Number of people responding 'To a great extent'",
       y = " ") + 
  theme_classic(base_size = 13) +
  theme(legend.position = "none",
        strip.text = element_text(face = 'bold'),
        panel.grid.major.x = element_line()) +
  scale_y_discrete(breaks = c("inf1", "inf2", "inf3", "inf4", "inf5", "inf6", "inf7", "inf10",
                              "inf11", "inf12", "inf13", "inf14", "inf15", "inf16", "inf17", "inf18"),
                   labels = c("Trust in vaccine company",
                              "Info of no side effects",
                              "Info about effectiveness",
                              "Personal high risk",
                              "Other's positive att.",
                              "Others getting vaccine",
                              "Doctor recommendation",
                              "Convenience of getting vaccine",
                              "Protect others",
                              "Attending events",
                              "Doing my part",
                              "Employer recommendation",
                              "Only need 1 dose",
                              "Reduce my worries",
                              "Effective for variants",
                              "Vaccine of choice")) +
  scale_fill_viridis_d()

yes <- survey_10 %>%
  filter(country_iso == "CANADA") %>%
  select(cvdvacci, contains("inflvac"), contains("inflvade")) %>%
  select_all(tolower) %>%
  mutate(inf1 = coalesce(inflvac_sq001, inflvade_sq001),
         inf2 = coalesce(inflvac_sq002, inflvade_sq002),
         inf3 = coalesce(inflvac_sq003, inflvade_sq003),
         inf4 = coalesce(inflvac_sq004, inflvade_sq004),
         inf5 = coalesce(inflvac_sq005, inflvade_sq005),
         inf6 = coalesce(inflvac_sq006, inflvade_sq006),
         inf7 = coalesce(inflvac_sq007, inflvade_sq007),
         inf10 = coalesce(inflvac_sq010, inflvade_sq010),
         inf11 = coalesce(inflvac_sq011, inflvade_sq011),
         inf12 = coalesce(inflvac_sq012, inflvade_sq012),
         inf13 = coalesce(inflvac_sq013, inflvade_sq013),
         inf14 = coalesce(inflvac_sq014, inflvade_sq014),
         inf15 = coalesce(inflvac_sq015, inflvade_sq015),
         inf16 = coalesce(inflvac_sq016, inflvade_sq016),
         inf17 = coalesce(inflvac_sq017, inflvade_sq017),
         inf18 = coalesce(inflvac_sq018, inflvade_sq018),
         vaccine = factor(cvdvacci, 
                          levels = c(1:5),
                          labels = c("No",
                                     "Yes (partially)",
                                     "Yes (fully)",
                                     "Yes (fully)",
                                     "Pref. not to answer"))) %>%
  filter(vaccine == "Yes (partially)" | vaccine == "Yes (fully)") %>%
  mutate_at(vars(c(inf1:inf18)), 
            funs(case_when(. == 1 ~ 1,
                           . == 2 | . == 3 | . == 4 ~ 0))) %>%
  pivot_longer(names_to = "influence", values_to = "value", cols = c(inf1:inf18)) %>%
  group_by(influence, value) %>%
  count(influence) %>%
  drop_na() %>%
  ungroup(influence, value) %>%
  filter(value == 1) %>%
  select(-value) %>%
  mutate(influence = as.factor(influence),
         influence = fct_reorder(influence, n)) %>%
  ggplot(aes(x = n, y = influence, fill = influence)) + 
  geom_col() + 
  labs(title = "VACCINATED (partially or fully)", 
       x = "Number of people responding 'To a great extent'",
       y = " ") + 
  theme_classic(base_size = 13) +
  theme(legend.position = "none",
        strip.text = element_text(face = 'bold'),
        panel.grid.major.x = element_line()) +
  scale_y_discrete(breaks = c("inf1", "inf2", "inf3", "inf4", "inf5", "inf6", "inf7", "inf10",
                              "inf11", "inf12", "inf13", "inf14", "inf15", "inf16", "inf17", "inf18"),
                   labels = c("Trust in vaccine company",
                              "Info of no side effects",
                              "Info about effectiveness",
                              "Personal high risk",
                              "Other's positive att.",
                              "Others getting vaccine",
                              "Doctor recommendation",
                              "Convenience of getting vaccine",
                              "Protect others",
                              "Attending events",
                              "Doing my part",
                              "Employer recommendation",
                              "Only need 1 dose",
                              "Reduce my worries",
                              "Effective for variants",
                              "Vaccine of choice")) +
  scale_fill_viridis_d()

(yes/no) + plot_annotation(tag_levels = 'A')
```

This document was prepared by UK - [reach me with any questions/comments](mailto:dr.urska.kosir@gmail.com)!