---
title: "Survey 11-13 Results"
author: " "
date: "Last update: `r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
library(here)
library(psych)
library(english)
library(stringr)
library(tableone)
library(kableExtra)
library(patchwork)
library(scales)
library(ggridges)
library(plotly)
library(haven)
```

```{r data, echo=FALSE, message=FALSE, warning=FALSE}
# Read in the raw SAS data file from the global sample
global_raw <- read_sas("survey_13/survey_1_13.sas7bdat") %>%
  select_all(tolower)

# Create a unique user ID (single digit)
global_raw <- rowid_to_column(global_raw)


global_raw$startdate2<-as.Date(global_raw$startdate)
global_raw$startdate2 <- factor(format(global_raw$startdate2,'%Y-%m')) ## Keep just month and year

global_raw$startdate3<-as.Date(global_raw$startdate)
global_raw$startdate3<- factor(format(global_raw$startdate3,'%Y-%m-%d')) ## Keep year, month, day

survey_13 <- global_raw %>%
  filter(wave %in% c(11:13)) %>%
  dplyr::select(rowid, immurec, immuinfl, startdate,
                cvdvacci, cvdvacc_v2, contrpos,
                vacboos,
         contains("inflvac"), contains("inflvade"),
         sex, age_yrs, edu, curemp, area, hoinc, contains("cemplstat")) %>%
  mutate(cempstat = case_when(cemplstat_sq001 == 0 ~ 1, ## Create a new variable for binary employment
                              cemplstat_sq001 == 1 ~ 2,
                              cemplstat_sq008 == 1 ~ 3),
        age_group = case_when(age_yrs <=25 ~ "under 25", 
                               age_yrs > 25 & age_yrs <51 ~ "26 - 50y",
                               age_yrs > 50 ~ "over 51"),
        sex = factor(sex, levels = c(1:4),
                      labels = c("male", "female", "other", "prefer not to answer")),
        area = factor(area, levels = c(1:4),
                      labels = c("rural", "suburban", "urban", "prefer not to answer")),
        employment = coalesce(curemp, cempstat), ## coalesce the values from survey 1-4 and the new variable created above..
        employment = factor(employment, 
                            levels = c(1:3),
                            labels = c("no", "yes", "prefer not to answer")),
        hoinc = factor(hoinc, 
                       levels = c(1:4),
                       labels = c("bottom 3rd", "middle 3rd", "top 3rd", "prefer not to answer")),
        edu = factor(edu, 
                     levels = c(1:6),
                     labels = c("primary", "secondary", "college", "graduate", "never been" ,"prefer not to answer")),
        vaccine = factor(cvdvacci, 
                          levels = c(1:5),
                          labels = c("No",
                                     "Yes (partially)",
                                     "Yes (fully)",
                                     "Yes (fully)",
                                     "Pref. not to answer")))
  
## QUICK FIX COPY AND PASTE FUNCTION instead of package -- working on this!

plot_pie_chart <- function(data,
                           variable,
                           filter_response = NULL,
                           title = NULL,
                           filllab = NULL,
                           labels = NULL,
                           number_font_size = 4,
                           return = c("plot", "data")) {

  return <- match.arg(return)

  data$month<-as.Date(data$startdate)
  data$month<- factor(format(data$month,'%Y-%m'))

  data_temp <- data %>%
    dplyr::select({{variable}}) %>%
    tidyr::pivot_longer(cols = {{variable}},
                 names_to = "variable") %>%
    dplyr::group_by(variable, value) %>%
    dplyr::count() %>%
    tidyr::drop_na() %>%
    dplyr::group_by(variable)%>%
    dplyr::mutate(sum_group = sum(n),
           prop = n / sum_group * 100)

  if(is.null(filter_response)) {
    data_temp <- data_temp
  } else
  {data_temp <- data_temp %>%
    dplyr::filter(value %in% filter_response)
  }
  # set the theme for the plot
  blank_theme <- ggplot2::theme_minimal()+
    ggplot2::theme(axis.title.x = ggplot2::element_blank(),
          axis.title.y = ggplot2::element_blank(),
          panel.border = ggplot2::element_blank(),
          panel.grid = ggplot2::element_blank(),
          axis.ticks = ggplot2::element_blank(),
          axis.text.x = ggplot2::element_blank(),
          plot.title = ggplot2::element_text(size = 15, hjust = 0.5, vjust = 1))

  plot <- data_temp %>%
    ggplot(aes(x =  "", y = n, fill = factor(value)))+
    geom_bar(stat = "identity") +
    coord_polar("y", start = 0)+
    labs(fill = filllab, title = title) +
    blank_theme +
    geom_text(aes(label = paste(round(n / sum(n) * 100, 1), "%")),
              color = "black", size = number_font_size,
              position = position_stack(vjust = 0.5))

  if(return == "data"){

    return(data_temp)

  }
  if(return == "plot"){
    if(is.null(labels)){
      return(plot)
    }else{
      return(plot + scale_fill_discrete(labels = labels))
    }
  }
}

```

# IMMUNIZATION PASSPORTS

## Immunization or vaccination passports have been suggested as a way to safely resume international travel. 
## How do you feel about the idea of using an immunization or vaccination passports?

```{r fig.width=8, fig.height=6, echo=FALSE, message=FALSE}
global_raw %>%
  filter(wave %in% c(11:13)) %>%
  select(immurec) %>%   # immuinfl
  drop_na() %>%
  filter(immurec %in% c(1:4)) %>%
  pivot_longer(cols = immurec,
               names_to = "var", 
               values_to = "response") %>%
  ggplot(aes(x = response, 
             y = (..count..)/1381,
             fill = factor(response))) +
  scale_y_continuous(labels=scales::percent, limits = c(0,0.75)) +
  geom_bar() +
  scale_x_continuous(breaks = c(1,2,3,4),
                   labels = c("Strongly in favor", "Moderately in favor", "Moderately against", "Strongly against")) +
  theme_bw() +
  scale_fill_viridis_d()+
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = " ",
       y = " Proportion",
       title = "Immunity passport attitudes (N = 1,381)")

```

### Table corresponding to the graph above

1 = Strongly in favor

```{r echo=FALSE, message=FALSE}
global_raw %>%
  filter(wave %in% c(11:13)) %>%
  select(immurec) %>%   # immuinfl
  drop_na() %>%
  filter(immurec %in% c(1:4)) %>%
  group_by(immurec) %>%
  count() %>%
  ungroup() %>%
  mutate(sum = sum(n),
         prop = (n/sum)*100,
         prop = round(prop, 2)) %>%
  dplyr::select(-sum) %>%
  kable() %>%
  kable_styling(full_width = FALSE)
```

## ATTITUDES BY DEMOGRAPHICS

We would like to have the above plotted by various demographics, the numbers are shown below in separate tables.
Bar plots would be great like the one above, perhaps different categories to be presented side by side. 
We would like to include proportion numbers in the plots as well.

Each table shows the number of responses to each level within each category - prop stands for proportion of responses within a given category (e.g. male).

### SEX
```{r echo=FALSE, warning=FALSE}
survey_13 %>%
  filter(immurec %in% c(1:4)) %>%
  mutate(immurec = factor(immurec, 
                          levels = c(1:4),
                          labels = c("strongly in favor", "moderately in favor", "moderately against", "strongly against"))) %>%
  filter(sex %in% c("male", "female")) %>%
  group_by(sex, immurec) %>%
  count() %>%
  group_by(sex) %>%
  mutate(sum = sum(n),
         prop = n/sum,
         prop = round(prop, 2)) %>%
  ungroup() %>%
  select(-sum) %>%
  kable() %>%
  kable_styling("hover", full_width = FALSE)
```

### AGE GROUP
```{r echo=FALSE, warning=FALSE}
survey_13 %>%
  filter(immurec %in% c(1:4)) %>%
  mutate(immurec = factor(immurec, 
                          levels = c(1:4),
                          labels = c("strongly in favor", "moderately in favor", "moderately against", "strongly against"))) %>%
  filter(age_group %in% c("under 25", "26 - 50y","over 51")) %>%
  group_by(age_group, immurec) %>%
  count() %>%
  group_by(age_group) %>%
  mutate(sum = sum(n),
         prop = (n/sum)*100,
         prop = round(prop, 2)) %>%
  ungroup() %>%
  select(-sum) %>%
  kable() %>%
  kable_styling("hover", full_width = FALSE)
```

### EDUCATION
```{r echo=FALSE, warning=FALSE}
survey_13 %>%
  filter(immurec %in% c(1:4)) %>%
  mutate(immurec = factor(immurec, 
                          levels = c(1:4),
                          labels = c("strongly in favor", "moderately in favor", "moderately against", "strongly against"))) %>%
  filter(edu %in% c("primary", "secondary", "college", "graduate", "never been")) %>%
  group_by(edu, immurec) %>%
  count() %>%
  group_by(edu) %>%
  mutate(sum = sum(n),
         prop = (n/sum)*100,
         prop = round(prop, 2)) %>%
  ungroup() %>%
  select(-sum) %>%
  kable() %>%
  kable_styling("hover", full_width = FALSE)
```

### INCOME
```{r echo=FALSE, warning=FALSE}
survey_13 %>%
  filter(immurec %in% c(1:4)) %>%
  mutate(immurec = factor(immurec, 
                          levels = c(1:4),
                          labels = c("strongly in favor", "moderately in favor", "moderately against", "strongly against"))) %>%
  filter(hoinc %in% c("bottom 3rd", "middle 3rd", "top 3rd")) %>%
  group_by(hoinc, immurec) %>%
  count() %>%
  group_by(hoinc) %>%
  mutate(sum = sum(n),
         prop = (n/sum)*100,
         prop = round(prop, 2)) %>%
  ungroup() %>%
  select(-sum) %>%
  kable() %>%
  kable_styling("hover", full_width = FALSE)
```

***

## To what extent would the introduction of ‘immunity passports’ influence your decision to get vaccinated?

Same as above, the plot below shows the overall sample, the subsequesnt tables are breaking it down by the demographic variables

```{r fig.width=8, fig.height=6, echo=FALSE, message=FALSE}
global_raw %>%
  filter(wave %in% c(11:13)) %>%
  select(immuinfl) %>%  
  drop_na() %>%
  filter(immuinfl %in% c(1:3)) %>%
  pivot_longer(cols = immuinfl,
               names_to = "var", 
               values_to = "response") %>%
  ggplot(aes(x = response, 
             y = (..count..)/1311,
             fill = factor(response))) +
  scale_y_continuous(labels=scales::percent, limits = c(0,0.75)) +
  geom_bar() +
  scale_x_continuous(breaks = c(1,2,3),
                   labels = c("More likely to get vaccinated", "No influence", "Less likely to get vaccinated")) +
  theme_bw() +
  scale_fill_viridis_d()+
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = " ",
       y = " Proportion",
       title = "Immunity passport influence on getting vaccinated (N = 1,311)")

```

### Table corresponding to the plot

1 = It would make me more likely to get vaccinated

```{r echo=FALSE, message=FALSE}
global_raw %>%
  filter(wave %in% c(11:13)) %>%
  select(immuinfl) %>%   # immuinfl
  drop_na() %>%
  filter(immuinfl %in% c(1:3)) %>%
  group_by(immuinfl) %>%
  count() %>%
  ungroup() %>%
  mutate(sum = sum(n),
         prop = (n/sum)*100,
         prop = round(prop, 2)) %>%
  kable() %>%
  kable_styling(full_width = FALSE)
```

### SEX
```{r echo=FALSE, warning=FALSE}
survey_13 %>%
  filter(immuinfl %in% c(1:3)) %>%
  mutate(immuinfl = factor(immuinfl, 
                          levels = c(1:3),
                          labels = c("more likely to get vaccinated", "no influence", "less likely"))) %>%
  filter(sex %in% c("male", "female")) %>%
  group_by(sex, immuinfl) %>%
  count() %>%
  group_by(sex) %>%
  mutate(sum = sum(n),
         prop = (n/sum)*100,
         prop = round(prop, 2)) %>%
  ungroup() %>%
  select(-sum) %>%
  kable() %>%
  kable_styling("hover", full_width = FALSE)
```

### AGE GROUP
```{r echo=FALSE, warning=FALSE}
survey_13 %>%
  filter(immuinfl %in% c(1:3)) %>%
  mutate(immuinfl = factor(immuinfl, 
                          levels = c(1:3),
                          labels = c("more likely to get vaccinated", "no influence", "less likely"))) %>%
  filter(age_group %in% c("under 25", "26 - 50y","over 51")) %>%
  group_by(age_group, immuinfl) %>%
  count() %>%
  group_by(age_group) %>%
  mutate(sum = sum(n),
         prop = (n/sum)*100,
         prop = round(prop, 2)) %>%
  ungroup() %>%
  select(-sum) %>%
  kable() %>%
  kable_styling("hover", full_width = FALSE)
```

### EDUCATION
```{r echo=FALSE, warning=FALSE}
survey_13 %>%
  filter(immuinfl %in% c(1:3)) %>%
  mutate(immuinfl = factor(immuinfl, 
                          levels = c(1:3),
                          labels = c("more likely to get vaccinated", "no influence", "less likely"))) %>%
  filter(edu %in% c("primary", "secondary", "college", "graduate", "never been")) %>%
  group_by(edu, immuinfl) %>%
  count() %>%
  group_by(edu) %>%
  mutate(sum = sum(n),
         prop = (n/sum)*100,
         prop = round(prop, 2)) %>%
  ungroup() %>%
  select(-sum) %>%
  kable() %>%
  kable_styling("hover", full_width = FALSE)
```

### INCOME
```{r echo=FALSE, warning=FALSE}
survey_13 %>%
  filter(immuinfl %in% c(1:3)) %>%
  mutate(immuinfl = factor(immuinfl, 
                          levels = c(1:3),
                          labels = c("more likely to get vaccinated", "no influence", "less likely"))) %>%
  filter(hoinc %in% c("bottom 3rd", "middle 3rd", "top 3rd")) %>%
  group_by(hoinc, immuinfl) %>%
  count() %>%
  group_by(hoinc) %>%
  mutate(sum = sum(n),
         prop = (n/sum)*100,
         prop = round(prop, 2)) %>%
  ungroup() %>%
  select(-sum) %>%
  kable() %>%
  kable_styling("hover", full_width = FALSE)
```
***
## Demographcics overall - WHO responded to surveys 11-13

This is mostly informative - given that the separate plots already break down the responses by demographics, this could just be place informatively at the bottom/smaller print.

Mind you that the numbers are only adding up to 1030 who provided the relevant information. 

### Sex

1 = male, 2 = female

```{r echo=FALSE, message=FALSE}
dems<-global_raw %>%
  filter(wave %in% c(11:13)) %>%
  select(sex, startdate, age_yrs, iso3_code, hoinc, immuinfl, immurec) %>%   # immuinfl
  drop_na(sex, startdate, age_yrs, iso3_code, hoinc) %>%
  filter(immuinfl %in% c(1:3)) %>%
  filter(immurec %in% c(1:4)) %>%
  mutate(age_group = case_when(age_yrs < 26 ~ 1,
                               age_yrs > 25 & age_yrs <56 ~ 2,
                               age_yrs > 55 ~ 3))

plot_pie_chart(data = dems,
               variable = sex,
               filter_response=c(1:2),
               title = "Sex distribution",
               labels = c("Male", "Female"),
               number_font_size = 6,
               return = "data")

```
### Age

age groups: 1 = under 26, 2 = 26-55y, 3 = over 55
```{r echo=FALSE, message=FALSE}
plot_pie_chart(data = dems,
               variable = age_group,
               filter_response=c(1:3),
               title = "Age groups",
               labels = c("under 26", " 26-55", "over 55"),
               number_font_size = 4,
               return = "data")
```

### Income

1 = lower 3rd, 2 = middle 3rd, 3 = upper 3rd
```{r echo=FALSE, message=FALSE}
plot_pie_chart(data = dems,
               variable = hoinc,
               filter_response=c(1:3),
               title = "Income distribution",
               labels = c("lower 3rd", "middle 3rd", "top 3rd"),
               number_font_size = 4,
               return = "data")
```

# Where are respondents from?

Countries with more than 20 respondents (% does not up to 100 because only top 10 countries are shown)
```{r echo=FALSE, message=FALSE}

dems %>%
  select(iso3_code) %>%
  group_by(iso3_code) %>%
  count() %>%
  ungroup() %>%
  mutate(sum = sum(n),
         prop = (n/sum)*100,
         prop = round(prop, 2),
         prop = paste0(prop, "%")) %>%
  filter(n>20) %>%
  select(-sum) %>%
  kable() %>%
  kable_styling(full_width = FALSE)
```

# ATTITUDES in CANADA (N = 453)

### How do you feel about the idea of using an immunization or vaccination passports?
```{r echo=FALSE, warning=FALSE}
global_raw %>%
  filter(wave %in% c(11:13)) %>%
  filter(iso3_code == "CAN") %>%
  select(immurec) %>%   # immuinfl
  drop_na() %>%
  filter(immurec %in% c(1:4)) %>%
  mutate(immurec = factor(immurec, 
                          levels = c(1:4),
                          labels = c("strongly in favor", "moderately in favor", "moderately against", "strongly against"))) %>%
  group_by(immurec) %>%
  count() %>%
  mutate(prop = (n/453)*100,
         prop = round(prop, 2)) %>%
  kable() %>%
  kable_styling(full_width = FALSE)
```

### To what extent would the introduction of ‘immunity passports’ influence your decision to get vaccinated?

```{r echo=FALSE, warning=FALSE}
global_raw %>%
    filter(wave %in% c(11:13)) %>%
  filter(iso3_code == "CAN") %>%
  select(immuinfl) %>%   # immuinfl
  drop_na() %>%
  filter(immuinfl %in% c(1:3)) %>%
  mutate(immuinfl = factor(immuinfl, 
                          levels = c(1:3),
                          labels = c("more likely to get vaccinated", "no influence", "less likely"))) %>%
  group_by(immuinfl) %>%
  count() %>%
  ungroup() %>%
  mutate(sum = sum(n),
         prop = (n/sum)*100,
         prop = round(prop, 2)) %>%
  kable() %>%
  kable_styling(full_width = FALSE)
```


## Vaccination rates in Sample 11 - 13

*NB* - proportion include missing data (NA)
```{r echo=FALSE, warning=FALSE}
survey_13 %>%
  select(vaccine) %>%
  group_by(vaccine) %>%
  count() %>%
  ungroup()%>%
  mutate(sum = sum(n),
         prop = (n/sum)*100,
         prop = round(prop, 2)) %>%
  ungroup() %>%
  select(-sum) %>%
  kable(col.names = c("Vaccinated?", "N", "Proportion")) %>%
  kable_styling("hover", full_width = FALSE)

```

### For those unvaccinated: If COVID-19 vaccine was available to you today, how likely are you to get it?

Only people who responded "No" to the question above (i.e. N = 261) are considered in this question.

**Based on these numbers we can assume that at least some of the respondents to the international survey still have trouble with accessing vaccine..

```{r echo=FALSE, warning=FALSE}
survey_13 %>%
  filter(vaccine == "No") %>%
  select(cvdvacc_v2) %>%
  mutate(vaccine_today = factor(cvdvacc_v2, 
                          levels = c(1:5),
                          labels = c("Extremely likely",
                                     "Somewhat likely",
                                     "Somewhat unlikely",
                                     "Extremely unlikely",
                                     "Pref. not to answer"))) %>%
  group_by(vaccine_today) %>%
  count() %>%
  ungroup() %>%
  mutate(sum = sum(n),
         prop = (n/sum)*100,
         prop = round(prop, 2)) %>%
  ungroup() %>%
  select(-sum) %>%
  kable(col.names = c("Likelihood", "N", "Proportion")) %>%
  kable_styling(full_width = FALSE)
```


### VACCINE BOOSTERS: If a booster dose of vaccine (an extra administration of a vaccine after an earlier dose) was required, how likely are you to get it? 

Missing data (NA values) are accounted for when calculating the proportion. 

There is a lot of missing data here...the question has only been administered to those fully vaccinated but the numbers still don't add up. I don't know why this may be.
```{r echo=FALSE, message=FALSE}
survey_13 %>%
  select(vacboos) %>%
  mutate(booster = factor(vacboos, 
                          levels = c(1:5),
                          labels = c("Extremely likely",
                                     "Somewhat likely",
                                     "Somewhat unlikely",
                                     "Extremely unlikely",
                                     "Pref. not to answer"))) %>%
  group_by(booster) %>%
  count() %>%
  ungroup() %>%
  mutate(sum = sum(n),
         prop = n/sum,
         prop = round(prop, 2)) %>%
  ungroup() %>%
  select(-sum) %>%
  kable(col.names = c("Likelihood", "N", "Proportion")) %>%
  kable_styling("hover", full_width = FALSE)

```
This document was prepared by UK - [reach me with any questions/comments](mailto:dr.urska.kosir@gmail.com)!