---
title: "RETURNING TO SCHOOL DURING A PANDEMIC: Canadian university students’ attitudes and concerns"
author: " "
date: "Last revision: May 5, 2021"
output: html_document
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
library(here)
library(psych)
library(english)
library(stringr)
library(tableone)
library(kableExtra)
library(patchwork)
library(scales)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(ggridges)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
# Read in the data
leger_student <- read_csv("~/Desktop/R Codes/leger-students/clean-data/leger_student.csv") %>%
  filter(student == 1)

peer_only<-read_csv("~/Desktop/R Codes/leger-students/clean-data/leger_student.csv") %>%
  filter(student == 0)

leger_s_w3w4<- leger_student %>%
  dplyr::filter(wave==3 | wave ==4 |wave==5) %>%
  rename(smode = stcursch) %>%
  tidyr::replace_na(list(any_m_health = 0)) %>%
  mutate(smode = factor(smode, levels = c(1:4),
                        labels = c("In-person only", "Hybrid", "Online only", "Other")),
         cov_imp_5a = as.factor(case_when(cov_imp_5==1|cov_imp_5==2~"Concerned",
                                          cov_imp_5==3|cov_imp_5==4~"Not concerned")),
         measures = factor(case_when(stmeas == 1 ~ "No measures",
                                        stmeas == 2 ~ "Too lenient",
                                        stmeas == 3 ~ "Just right",
                                        stmeas == 4 ~ "Too strict"),
                              ordered = TRUE)) %>%
  mutate(distress_r = 17-distress) %>%
  mutate(distress_r = distress_r + 3) %>%
  mutate(student = factor(student, levels = c(0:1),
                          labels = c("Non-student", "Student")),
         mh_diag = ifelse(any_m_health == 0, "no", "yes"),
         sex = factor(sex, levels = c(1:2),
                      labels = c("Male", "Female")))
  

leger_peer <- read_csv("~/Desktop/R Codes/leger-students/clean-data/leger-student-matched.csv") %>%
filter(student == 0)

complete <- read_csv("~/Desktop/R Codes/leger-students/clean-data/leger-student-matched.csv") %>%
  dplyr::select(rowid, distress, student, sex, weights, age_yrs, province, any_m_health) %>%
  tidyr::replace_na(list(any_m_health = 0))%>%
  mutate(distress_r = 17-distress) %>%
  mutate(distress_r = distress_r + 3) %>%
  mutate(student = factor(student, levels = c(0:1),
                          labels = c("Non-student", "Student")),
         mh_diag = ifelse(any_m_health == 0, "no", "yes"),
         sex = factor(sex, levels = c(1:2),
                      labels = c("Male", "Female")))

peer_table <- leger_peer %>%
  dplyr::select(employment) %>%
  mutate(employment = factor(employment, levels = c(1:8), labels = c("Retired", "Social assistance/Disability", "Unemployment", "Student", "Part-time", "Full-time", "Self-employed", "Other")))

## GET THE DEMS PROVINCE COUNTS (%)
s_prov_table <- as.data.frame(table(leger_s_w3w4$province_full))%>%
  mutate(pct = Freq/nrow(leger_s_w3w4)*100) %>%
  mutate(pct = round(pct, 0))

blank_theme <- theme_minimal()+
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    panel.border = element_blank(),
    panel.grid=element_blank(),
    axis.ticks = element_blank(),
    axis.text.x=element_blank(),
    #text = element_text('Times New Roman'),
    plot.title=element_text(size=15, hjust = 0.5, vjust = 1)
  )
```

## Return to school
The 2 tables are based on the complete answers of students who were studying at a distance and responded to the following questions:
Survey question w/ 4 point Likert scale (to a great extent, somewhat, little, not at all). The tables below collate To a great extent & somewhat into 1 category and little & not at all in the other category.

* My mental health would get worse: ___
* My mental health would improve: ___

I think this could be either presented as a piechart (see below) or as a bar plot.

```{r results='asis', echo=FALSE, message=FALSE, warning=FALSE}
# THOSE STUDYING ONLINE - MH GETTING BETTER
mh_worse_tab<-leger_s_w3w4 %>%
  filter(smode=="Online only") %>%
  mutate(mh_worse = case_when(stmimp_sq005 == 1 | stmimp_sq005 == 2 ~ "Deteriorate",
                              stmimp_sq005 == 3 | stmimp_sq005 == 4 ~ "Not deteriorate")) %>%
  count(mh_worse) 

mh_worse_tab%>%
  drop_na() %>%
  mutate(pct = n/sum(n)*100) %>%
  mutate(pct = round(pct, 0)) %>%
  kable(col.names = c("Expectation", "N", "%"),
        align = c("l", "c","c")) %>%
  kable_styling(full_width = FALSE)

# THOSE STUDYING ONLINE - MH GETTING BETTER
mh_better_tab<-leger_s_w3w4 %>%
  filter(smode=="Online only") %>%
  mutate(mh_better = case_when(stmimp_sq006 == 1 | stmimp_sq006 == 2 ~ "Improve",
                               stmimp_sq006 == 3 | stmimp_sq006 == 4 ~ "Not improve")) %>%
  count(mh_better)

mh_better_tab%>%
  drop_na() %>%
  mutate(pct = n/sum(n)*100) %>%
  mutate(pct = round(pct, 0)) %>%
  kable(col.names = c("Expectation", "N", "%"),
        align = c("l", "c","c")) %>%
  kable_styling(full_width = FALSE)

```

### EG: Proportion who expects their mental health to deteriorate

```{r echo=FALSE, message=FALSE, warning=FALSE}
mh_worse_tab %>%
  drop_na() %>%
      ggplot(aes(x=" ", y=n, fill=mh_worse))+
      geom_bar(stat = "identity") + #geom_col(position = 'stack', width = 1) - produces exactly the same thing
      coord_polar("y", start=0)+
      labs(fill = " ") +
      scale_fill_viridis_d(alpha = .8, begin = 0.1, end = 0.6) +
      blank_theme +
      geom_text(aes(label = paste(round(n/sum(n)*100, 1), "%")),
                color = "black", size=5,
                position = position_stack(vjust = 0.5))
    
```

### EG: Proportion who expects their mental health to improve

```{r echo=FALSE, message=FALSE, warning=FALSE}
mh_better_tab %>%
  drop_na() %>%
      ggplot(aes(x="", y=n, fill=mh_better))+
      geom_bar(stat = "identity") + #geom_col(position = 'stack', width = 1) - produces exactly the same thing
      coord_polar("y", start=0)+
      labs(fill = " ") +
      scale_fill_viridis_d(alpha = .8, begin = 0.1, end = 0.6) +
      blank_theme +
      geom_text(aes(label = paste(round(n/sum(n)*100, 1), "%")),
                color = "black", size=5,
                position = position_stack(vjust = 0.5))
    
```

## Compare Students to Non-student peers in MENTAL HEALTH

*NB* - To get the corresponding data table extracted uncomment the code in the .RMD file and re-run.

```{r results='asis', echo=FALSE, message=FALSE, warning=FALSE}
dat.compare <- read_csv("~/Desktop/R Codes/leger-students/clean-data/leger_student.csv") %>%
  dplyr::select(rowid, age_yrs, student, impacvd_sq001:impacvd_sq003) %>%
  mutate(age_group = as.factor(case_when(age_yrs < 26 ~ "Under 25",
                               age_yrs >= 26 & age_yrs < 36 ~ "25 - 35 years",
                               age_yrs > 35 ~ "Over 35")),
         student = factor(student, 
                          levels = c(0:1),
                          labels = c("Non-Student", "Student"))) %>%
  rename(Anxiety = impacvd_sq001,
         Depression = impacvd_sq002,
         Loneliness = impacvd_sq003)

dat.compare %>%
  #filter(age_group == "Under 25") %>%
  pivot_longer(cols = c(Anxiety, Depression, Loneliness), names_to = "variable") %>%
  group_by(student, variable, value) %>%
  count() %>%
  drop_na() %>%
  group_by(student, variable) %>%
  mutate(sum_group_status = sum(n),
         prop_greatextend = n / sum_group_status * 100,
         variable = stringr::str_to_sentence(variable)) %>%
  filter(value == 4) %>% # 4 is to a great extent
  ggplot(aes(x = student)) +
  geom_col(aes(y = prop_greatextend, fill = student)) +
  facet_wrap(~variable) +
      labs(title = "Proportion endorsing a great extent of impact", x = " ", y = "%") +
      ylim(0, 60) +
      scale_fill_viridis_d() +
      theme_bw() +
      theme(legend.position = "none",
            axis.text.x = element_text(angle = 45, hjust = 1))


#-------
# To get the data for the plot un-comment the below
# if wish to get proportion and numbers for all response categories then remove the filtering by value

# dat.compare %>%
#   pivot_longer(cols = c(Anxiety, Depression, Loneliness), names_to = "variable") %>%
#   group_by(student, variable, value) %>%
#   count() %>%
#   drop_na() %>%
#   group_by(student, variable) %>%
#   mutate(sum_group_status = sum(n),
#          prop_greatextend = n / sum_group_status * 100,
#          variable = stringr::str_to_sentence(variable)) %>%
#   filter(value == 4) %>%
#   kable()
```

\newpage

## MINI INFO BUBBLE: Who is most distressed among students

Adjusting for location, age, health, study mode and perceived income, female students and individuals with a diagnosis of an anxiety or mood disorders report greatest levels of overall psychological distress.


## Data source and description
The results about return to school are based on `r leger_s_w3w4 %>% nrow` responses from students from across Canada between November/December and Mid March.

The sample was `r round((leger_s_w3w4 %>% filter(sex == "Female") %>% nrow)/leger_s_w3w4 %>% nrow*100, 1)`% female. 

On average they are `r round(mean(leger_s_w3w4$age_yrs), 1)` years old (range `r min(leger_s_w3w4$age_yrs)` -- `r max(leger_s_w3w4$age_yrs)`).

From `r nrow(leger_s_w3w4)` respondents, `r leger_s_w3w4 %>% filter(smode == "In-person only") %>% nrow` attended school in person only, `r leger_s_w3w4 %>% filter(smode == "Hybrid") %>% nrow` were in a hybrid mode (attending in person as well as online), and `r leger_s_w3w4 %>% filter(smode == "Online only") %>% nrow` were learning at a distance only.

### Comparison groups in figures on p. 3:
Students were `r leger_student %>% nrow`, The sample was `r round((leger_student %>% filter(sex == 2) %>% nrow)/leger_student %>% nrow*100, 1)`% female, aged `r round(mean(leger_student$age_yrs), 1)` years on average (range `r min(leger_student$age_yrs)` -- `r max(leger_student$age_yrs)`).

Non-student peers were `r peer_only %>% nrow`, The sample was `r round((peer_only %>% filter(sex == 2) %>% nrow)/peer_only %>% nrow*100, 1)`% female, aged `r round(mean(peer_only$age_yrs), 1)` years on average (range `r min(peer_only$age_yrs)` -- `r max(peer_only$age_yrs)`).

*** 

This document was prepared by UK - [reach me with any questions/comments](mailto:dr.urska.kosir@gmail.com)!