---
title: "Infographic: vaccine motivations"
author: " "
date: "Last update: `r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
library(here)
library(psych)
library(english)
library(stringr)
library(tableone)
library(kableExtra)
library(patchwork)
library(scales)
library(sjlabelled)
library(ggridges)
library(plotly)
library(patchwork)
```

```{r data, echo=FALSE, message=FALSE, warning=FALSE}
# Read in the raw SAS data file from the global sample
global_raw <- read_sas("survey_10/wave_10.sas7bdat") %>%
  select_all(tolower)

# Create a unique user ID (single digit)
global_raw <- rowid_to_column(global_raw)


global_raw$startdate2<-as.Date(global_raw$startdate)
global_raw$startdate2<- factor(format(global_raw$startdate2,'%Y-%m')) ## Keep just month and year

global_raw$startdate3 <- as.Date(global_raw$startdate)
global_raw$startdate3<- factor(format(global_raw$startdate3,'%Y-%m-%d')) ## Keep year, month, day

survey_9_10 <- global_raw %>%
  filter(wave == 10) %>%
  select(rowid, immurec, immuinfl, startdate, country_iso,
         cvdvacci, cvdvacc_v2, contrpos,
         contains("inflvac"), contains("inflvade"),
         sex, age_yrs, edu, curemp, area, hoinc, contains("cempstat")) %>%
  mutate(cempstat = case_when(cempstat_sq001 == 0 ~ 1, ## Create a new variable for binary employment
                              cempstat_sq001 == 1 ~ 2,
                              cempstat_sq008 == 1 ~ 3),
        age_group = case_when(age_yrs <=25 ~ "under 25", 
                               age_yrs > 25 & age_yrs <51 ~ "26 - 50y",
                               age_yrs > 50 ~ "over 51"),
        sex = factor(sex, levels = c(1:4),
                      labels = c("male", "female", "other", "prefer not to answer")),
        area = factor(area, levels = c(1:4),
                      labels = c("rural", "suburban", "urban", "prefer not to answer")),
        employment = coalesce(curemp, cempstat), ## coalesce the values from survey 1-4 and the new variable created above..
        employment = factor(employment, 
                            levels = c(1:3),
                            labels = c("no", "yes", "prefer not to answer")),
        hoinc = factor(hoinc, 
                       levels = c(1:4),
                       labels = c("bottom 3rd", "middle 3rd", "top 3rd", "prefer not to answer")),
        edu = factor(edu, 
                     levels = c(1:6),
                     labels = c("primary", "secondary", "college", "graduate", "never been" ,"prefer not to answer"))
         )
  
```

## GLOBAL SAMPLE

### Have you received a COVID-19 vaccine?

Responses collected during April, May and June:
(NA = missing data)

```{r echo=FALSE, warning=FALSE}
survey_9_10 %>%
  select(cvdvacci) %>%
  mutate(vaccine = factor(cvdvacci, 
                          levels = c(1:5),
                          labels = c("No",
                                     "Yes (partially)",
                                     "Yes (fully)",
                                     "Yes (fully)",
                                     "Pref. not to answer"))) %>%
  group_by(vaccine) %>%
  count() %>%
  ungroup() %>%
  mutate(sum = sum(n),
         prop = n/sum,
         prop = round(prop, 2)) %>%
  ungroup() %>%
  select(-sum) %>%
  kable() %>%
  kable_styling(full_width = FALSE)

```

### If COVID-19 vaccine was available to you today, how likely are you to get it?

Out of those who have reported not yet being vaccinated, the majority reported positive intention.

```{r echo=FALSE, warning=FALSE}
survey_9_10 %>%
  select(cvdvacc_v2) %>%
  mutate(vaccine_today = factor(cvdvacc_v2, 
                          levels = c(1:5),
                          labels = c("Extremely likely",
                                     "Somewhat likely",
                                     "Somewhat unlikely",
                                     "Extremely unlikely",
                                     "Pref. not to answer"))) %>%
  group_by(vaccine_today) %>%
  drop_na() %>%
  count() %>%
  ungroup() %>%
  mutate(sum = sum(n),
         prop = n/sum,
         prop = round(prop, 2)) %>%
  ungroup() %>%
  select(-sum) %>%
  kable() %>%
  kable_styling(full_width = FALSE)
```

### What does/would greatly impact your choice for getting the COVID-19 vaccine?

We wanted to showcase the differences in motivations between those who are vaccinated versus not.

```{r echo=FALSE, warning=FALSE, fig.width=7, fig.height=10}
# Create data for the plots A and B

bar_plot_data <- survey_9_10 %>%
  select(cvdvacci, contains("inflvac"), contains("inflvade")) %>%
  select_all(tolower) %>%
  mutate(inf1 = coalesce(inflvac_sq001, inflvade_sq001),
         inf2 = coalesce(inflvac_sq002, inflvade_sq002),
         inf3 = coalesce(inflvac_sq003, inflvade_sq003),
         inf4 = coalesce(inflvac_sq004, inflvade_sq004),
         inf5 = coalesce(inflvac_sq005, inflvade_sq005),
         inf6 = coalesce(inflvac_sq006, inflvade_sq006),
         inf7 = coalesce(inflvac_sq007, inflvade_sq007),
         inf10 = coalesce(inflvac_sq010, inflvade_sq010),
         inf11 = coalesce(inflvac_sq011, inflvade_sq011),
         inf12 = coalesce(inflvac_sq012, inflvade_sq012),
         inf13 = coalesce(inflvac_sq013, inflvade_sq013),
         inf14 = coalesce(inflvac_sq014, inflvade_sq014),
         inf15 = coalesce(inflvac_sq015, inflvade_sq015),
         inf16 = coalesce(inflvac_sq016, inflvade_sq016),
         inf17 = coalesce(inflvac_sq017, inflvade_sq017),
         inf18 = coalesce(inflvac_sq018, inflvade_sq018),
         vaccine = factor(cvdvacci, 
                          levels = c(1:5),
                          labels = c("No",
                                     "Yes (partially)",
                                     "Yes (fully)",
                                     "Yes (fully)",
                                     "Pref. not to answer")))
# Common theme
plot_theme <- theme_classic(base_size = 13) +
  theme(legend.position = "none",
        strip.text = element_text(face = 'bold'),
        panel.grid.major.x = element_line())

# Common labels 
plot_label <- scale_y_discrete(breaks = c("inf1", "inf2", "inf3", "inf4", "inf5", "inf6", "inf7", "inf10",
                              "inf11", "inf12", "inf13", "inf14", "inf15", "inf16", "inf17", "inf18"),
                   labels = c("Trust in vaccine company",
                              "Info of no side effects",
                              "Info about effectiveness",
                              "Personal high risk",
                              "Other's positive att.",
                              "Others getting vaccine",
                              "Doctor recommendation",
                              "Convenience of getting vaccine",
                              "Protect others",
                              "Attending events",
                              "Doing my part",
                              "Employer recommendation",
                              "Only need 1 dose",
                              "Reduce my worries",
                              "Effective for variants",
                              "Vaccine of choice"))
## To a great extent
no <-  bar_plot_data %>%
  filter(vaccine == "No") %>%
  mutate_at(vars(c(inf1:inf18)), 
            funs(case_when(. == 1 ~ 1,
                           . == 2 | . == 3 | . == 4 ~ 0))) %>%
  pivot_longer(names_to = "influence", values_to = "value", cols = c(inf1:inf18)) %>%
  group_by(influence, value) %>%
  count(influence) %>%
  drop_na() %>%
  ungroup(influence, value) %>%
  filter(value == 1) %>%
  select(-value) %>%
  mutate(influence = as.factor(influence),
         influence = fct_reorder(influence, n)) %>%
  ggplot(aes(x = n, y = influence, fill = influence)) + 
  geom_col() + 
  labs(title = "UNVACCINATED INDIVIDUALS (N = 434)", 
       x = "Number of people responding 'To a great extent'",
       y = " ") + 
  plot_theme +
  plot_label +
  scale_fill_viridis_d()

yes <- bar_plot_data %>%
  filter(vaccine == "Yes (partially)" | vaccine == "Yes (fully)") %>%
  mutate_at(vars(c(inf1:inf18)), 
            funs(case_when(. == 1 ~ 1,
                           . == 2 | . == 3 | . == 4 ~ 0))) %>%
  pivot_longer(names_to = "influence", values_to = "value", cols = c(inf1:inf18)) %>%
  group_by(influence, value) %>%
  count(influence) %>%
  drop_na() %>%
  ungroup(influence, value) %>%
  filter(value == 1) %>%
  select(-value) %>%
  mutate(influence = as.factor(influence),
         influence = fct_reorder(influence, n)) %>%
  ggplot(aes(x = n, y = influence, fill = influence)) + 
  geom_col() + 
  labs(title = "VACCINATED (partially or fully) (N = 643)", 
       x = "Number of people responding 'To a great extent'",
       y = " ") + 
  plot_theme +
  plot_label +
  scale_fill_viridis_d()

(yes/no) + plot_annotation(tag_levels = 'A')

bar_plot_data2 <- survey_9_10 %>%
  select(cvdvacci, contains("inflvac"), contains("inflvade")) %>%
  select_all(tolower) %>%
  mutate(Trust_in_vaccine_company = coalesce(inflvac_sq001, inflvade_sq001),
         Info_of_no_side_effects = coalesce(inflvac_sq002, inflvade_sq002),
         Info_about_effectiveness = coalesce(inflvac_sq003, inflvade_sq003),
         Personal_high_risk = coalesce(inflvac_sq004, inflvade_sq004),
         Others_positive_att = coalesce(inflvac_sq005, inflvade_sq005),
         Others_getting_vaccine = coalesce(inflvac_sq006, inflvade_sq006),
         Doctor_recommendation = coalesce(inflvac_sq007, inflvade_sq007),
         Convenience_of_getting_vaccine = coalesce(inflvac_sq010, inflvade_sq010),
         Protect_others = coalesce(inflvac_sq011, inflvade_sq011),
         Attending_events = coalesce(inflvac_sq012, inflvade_sq012),
         Doing_my_part = coalesce(inflvac_sq013, inflvade_sq013),
         Employer_recommendation = coalesce(inflvac_sq014, inflvade_sq014),
         Only_need_1_dose = coalesce(inflvac_sq015, inflvade_sq015),
         Reduce_my_worries = coalesce(inflvac_sq016, inflvade_sq016),
         Effective_for_variants = coalesce(inflvac_sq017, inflvade_sq017),
         Vaccine_of_choice = coalesce(inflvac_sq018, inflvade_sq018),
         vaccine = factor(cvdvacci, 
                          levels = c(1:5),
                          labels = c("No",
                                     "Yes (partially)",
                                     "Yes (fully)",
                                     "Yes (fully)",
                                     "Pref. not to answer")))
```


```{r echo=FALSE, warning=FALSE, fig.width=7, fig.height=10}

no2 <-  bar_plot_data2 %>%
  filter(vaccine == "No") %>%
  mutate_at(vars(c(Trust_in_vaccine_company:Vaccine_of_choice)), 
            funs(case_when(. == 1 ~ 1,
                           . == 2 | . == 3 | . == 4 ~ 0))) %>%
  pivot_longer(names_to = "influence", 
               values_to = "value", 
               cols = c(Trust_in_vaccine_company:Vaccine_of_choice)) %>%
  group_by(influence, value) %>%
  count(influence) %>%
  drop_na() %>%
  ungroup(influence, value) %>%
  filter(value == 1) %>%
  select(-value) %>%
  mutate(influence = as.factor(influence),
         influence = fct_reorder(influence, n)) %>%
  ggplot(aes(x = n, y = influence, fill = influence)) + 
  geom_col() + 
  labs(title = "UNVACCINATED INDIVIDUALS (N = 434)", 
       x = "Number of people responding 'To a great extent'",
       y = " ") + 
  plot_theme +
  scale_fill_viridis_d(option = "D", begin = 0.3) +
  geom_text(aes(label = n))

yes2 <- bar_plot_data2 %>%
  filter(vaccine == "Yes (partially)" | vaccine == "Yes (fully)") %>%
  mutate_at(vars(c(Trust_in_vaccine_company:Vaccine_of_choice)), 
            funs(case_when(. == 1 ~ 1,
                           . == 2 | . == 3 | . == 4 ~ 0))) %>%
  pivot_longer(names_to = "influence", 
               values_to = "value", 
               cols = c(Trust_in_vaccine_company:Vaccine_of_choice)) %>%
  group_by(influence, value) %>%
  count(influence) %>%
  drop_na() %>%
  ungroup(influence, value) %>%
  filter(value == 1) %>%
  select(-value) %>%
  mutate(influence = as.factor(influence),
         influence = fct_reorder(influence, n)) %>%
  ggplot(aes(x = n, y = influence, fill = influence)) + 
  geom_col() + 
  labs(title = "VACCINATED (partially or fully) (N = 643)", 
       x = "Number of people responding 'To a great extent'",
       y = " ") + 
  plot_theme +
  scale_fill_viridis_d(option = "D", begin = 0.3) +
  geom_text(aes(label = n))

(yes2/no2) + plot_annotation(tag_levels = 'A')

```

In order to extract the raw data for the corresponding plots uncomment the code below (in the script) and re-run it. 
<!-- ## Data for the plots -->
<!-- #### Figure A -->
```{r echo=FALSE, message=FALSE, warning=FALSE}
# ## To a great extent
# bar_plot_data %>%
#   filter(vaccine == "No") %>%
#   mutate_at(vars(c(inf1:inf18)), 
#             funs(case_when(. == 1 ~ 1,
#                            . == 2 | . == 3 | . == 4 ~ 0))) %>%
#   pivot_longer(names_to = "influence", values_to = "value", cols = c(inf1:inf18)) %>%
#   group_by(influence, value) %>%
#   count(influence) %>%
#   drop_na() %>%
#   ungroup(influence, value) %>%
#   filter(value == 1) %>%
#   select(-value) %>%
#   mutate(influence = as.factor(influence),
#          influence = fct_reorder(influence, n)) %>%
#   kable() %>%
#   kable_styling(full_width = FALSE)
```

<!-- #### Figure B -->
```{r echo=FALSE, message=FALSE, warning=FALSE}
# ## To a great extent
# bar_plot_data %>%
#   filter(vaccine == "Yes (partially)" | vaccine == "Yes (fully)") %>%
#   mutate_at(vars(c(inf1:inf18)), 
#             funs(case_when(. == 1 ~ 1,
#                            . == 2 | . == 3 | . == 4 ~ 0))) %>%
#   pivot_longer(names_to = "influence", values_to = "value", cols = c(inf1:inf18)) %>%
#   group_by(influence, value) %>%
#   count(influence) %>%
#   drop_na() %>%
#   ungroup(influence, value) %>%
#   filter(value == 1) %>%
#   select(-value) %>%
#   mutate(influence = as.factor(influence),
#          influence = fct_reorder(influence, n)) %>%
#   kable() %>%
#   kable_styling(full_width = FALSE)
```

<!-- #### Respondents were from the following countries: -->

<!-- *NOTE*: Only showing countries with at least 20 participants -->

<!-- Empty cell (N=88) - origin not known -->

```{r echo=FALSE, message=FALSE}

# survey_9_10 %>%
#   select(country_iso) %>%
#   group_by(country_iso) %>%
#   count() %>%
#   ungroup() %>%
#   mutate(sum = sum(n),
#          prop = (n/sum)*100,
#          prop = round(prop, 2),
#          prop = paste0(prop, "%")) %>%
#   filter(n>20) %>%
#   select(-sum) %>%
#   kable() %>%
#   kable_styling(full_width = FALSE)
```


This document was prepared by UK - [reach me with any questions/comments](mailto:dr.urska.kosir@gmail.com)!